---
title: "Enrolment and Baseline"
description: |
  Exploratory summaries of enrolment and baseline data.
author: "James Totterdell"
date: today
execute: 
  echo: false
  message: false
  warning: false
---

```{r}
#| label: pkgs
#| include: false
library(tidyverse)
library(kableExtra)
library(labelled)
library(lubridate)
library(patchwork)
library(ASCOTr)

theme_set(theme_classic(base_size = 10, base_family = "Palatino") +
  theme(panel.grid = element_blank(),
        strip.background = element_blank()))
```

```{r}
#| label: load-data
all_data <- readRDS(file.path(ASCOT_DATA, "all_data.rds"))
all_daily_data <- readRDS(file.path(ASCOT_DATA, "all_daily_data.rds"))
pd <- readRDS(file.path(ASCOT_DATA, "pd.rds"))

# FAS-ITT
fas_itt_dat <- ASCOTr:::make_fas_itt_set(all_data)
fas_itt_nona_dat <- fas_itt_dat |>
  filter(!is.na(PO))

# ACS-ITT
acs_itt_dat <- ASCOTr:::make_acs_itt_set(all_data)
acs_itt_nona_dat <- acs_itt_dat |>
  filter(!is.na(PO))

# AVS-ITT
avs_itt_dat <- ASCOTr:::make_avs_itt_set(all_data)
avs_itt_nona_dat <- avs_itt_dat |>
  filter(!is.na(PO))

# FAS-ITT Best Case/Worst case
fas_itt_bc_dat <- fas_itt_dat |>
  mutate(PO = if_else(is.na(PO), 0, PO))
fas_itt_wc_dat <- fas_itt_dat |>
  mutate(PO = if_else(is.na(PO), 1, PO))

# FAS-PP
fas_pp_dat <- fas_itt_dat |>
  left_join(pd, by = "StudyPatientID") |>
  filter(is.na(pd_A) | pd_A == 0, is.na(pd_C) | pd_C == 0)
fas_pp_nona_dat <- fas_pp_dat |>
  filter(!is.na(PO))

# ACS-PP
acs_pp_dat <- acs_itt_dat |>
  left_join(pd, by = "StudyPatientID") |>
  filter(is.na(pd_C) | pd_C == 0)
acs_pp_nona_dat <- acs_pp_dat |>
  filter(!is.na(PO))

# AVS-PP
avs_pp_dat <- avs_itt_dat |>
  left_join(pd, by = "StudyPatientID") |>
  filter(is.na(pd_A) | pd_A == 0)
avs_pp_nona_dat <- avs_pp_dat |>
  filter(!is.na(PO))
```

# Enrolment

```{r}
#| label: fig-enrolment
#| code-summary: Study enrolment
#| fig-cap-location: margin
#| fig-cap: |
#|   Cumulative enrolments to the platform, 
#|   vertical lines indicate timing of interim analyses
#| fig-height: 7
md <- get_interim_dates()
id <- get_intervention_dates()
dt_rng <- range(all_data$RandDate, na.rm = TRUE)

p1 <- all_data %>%
  filter(ENR_rec == 1) %>%
  dplyr::count(RandDate) %>%
  complete(RandDate = seq.Date(dt_rng[1], dt_rng[2], by = "1 day"),
           fill = list(n = 0)) %>%
  mutate(`Cumulative enrolments` = cumsum(n)) %>%
  rename(`Randomisation date` = RandDate) %>%
  ggplot(., aes(`Randomisation date`, `Cumulative enrolments`)) +
  geom_step() +
  geom_vline(data = md,
             aes(xintercept = as.numeric(meet_date)),
             linetype = 2) +
  labs(x = "", subtitle = "Cumulative enrolments", y = "") +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y")

pA <- all_data %>%
  filter(ENR_rec == 1, AAssignment != "A0") %>%
  count(RandDate) %>%
  complete(RandDate = seq.Date(dt_rng[1], dt_rng[2], by = "1 day"),
           fill = list(n = 0)) %>%
  mutate(`Cumulative enrolments` = cumsum(n)) %>%
  rename(`Randomisation date` = RandDate) %>%
  ggplot(., aes(`Randomisation date`, `Cumulative enrolments`)) +
  geom_step() +
  geom_vline(data = md,
             aes(xintercept = as.numeric(meet_date)),
             linetype = 2) +
  labs(x = "", subtitle = "Cumulative enrolments in antiviral domain", y = "") +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y")

pC <- all_data %>%
  filter(ENR_rec == 1, CAssignment != "C0") %>%
  count(RandDate) %>%
  complete(RandDate = seq.Date(dt_rng[1], dt_rng[2], by = "1 day"),
           fill = list(n = 0)) %>%
  mutate(`Cumulative enrolments` = cumsum(n)) %>%
  rename(`Randomisation date` = RandDate) %>%
  ggplot(., aes(`Randomisation date`, `Cumulative enrolments`)) +
  geom_step() +
  geom_vline(data = md,
             aes(xintercept = as.numeric(meet_date)),
             linetype = 2) +
  labs(x = "", subtitle = "Cumulative enrolments in anticoagulation domain", y = "") +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y")

p2 <- id %>%
  mutate(
    Intervention = factor(Intervention, labels = unlist(intervention_labels2())[-c(1, 4)])
  ) %>%
  ggplot(.) +
  facet_grid(Domain ~ ., drop = TRUE, scales = "free_y", space = "free_y") +
  geom_point(aes(x = Intervention, y = endate), shape = 4) +
  geom_segment(
    aes(x = Intervention, xend = Intervention, 
        y = stdate, yend = endate))  +
  geom_hline(data = md,
             aes(yintercept = as.numeric(meet_date)),
             linetype = 2) +
  coord_flip() +
  labs(x = "", y = "Calendar date", subtitle = "Available interventions") +
  scale_y_date(date_breaks = "3 months", date_labels = "%b %Y")

p <- pA / pC / p2
pth <- file.path("outputs", "figures", "baseline")
ggsave(file.path(pth, "enrolment-domain.pdf"), p, height = 6, width = 6)
p
```

# Intervention Assignments

```{r}
#| label: tbl-intervention-assignments-anticoagulation
#| tbl-cap: Counts of intervention assignments to anticoagulation domain.
#| tbl-cap-location: margin
all_data |>
  filter_fas_itt() |>
  dplyr::count(FAS_ITT, ACS_ITT, CAssignment) |>
  kable() |>
  kable_styling("striped", font_size = 12)
```

```{r}
#| label: tbl-intervention-assignments-antiviral
#| tbl-cap: Counts of intervention assignments to antiviral domain.
#| tbl-cap-location: margin
all_data |>
  filter_fas_itt() |>
  dplyr::count(FAS_ITT, AVS_ITT, AAssignment) |>
  kable() |>
  kable_styling("striped", font_size = 12)
```

```{r}
#| label: tbl-interventions-fas-itt
#| tbl-cap: Distribution of interventions assigned to participants, FAS-ITT.
#| cap-location: margin
tab <- make_intervention_table(all_data |> filter(ENR_rec == 1, FAS_ITT == 1))
savetab <- tab |>
  kable("latex", align = "lrrrr", booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 10) |>
  add_header_above(c(" " = 1, "Antiviral" = 3, " " = 1))
save_tex_table(
  savetab, 
  fn = file.path("baseline", "fas-itt-interventions")
)
tab |>
  kable("html", align = "lrrrr") |>
  kable_styling("striped", font_size = 12) |>
  add_header_above(c(" " = 1, "Antiviral" = 3, " " = 1))
```

```{r}
#| label: tbl-interventions-acs-itt
#| tbl-cap: Distribution of interventions assigned to participants, ACS-ITT.
#| cap-location: margin
tab <- make_intervention_table(all_data |> filter(ENR_rec == 1, ACS_ITT == 1))
savetab <- tab |>
  kable("latex", align = "lrrrr", booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 10) |>
  add_header_above(c(" " = 1, "Antiviral" = 3, " " = 1))
save_tex_table(
  savetab, 
  fn = file.path("baseline", "acs-itt-interventions")
)
tab |>
  kable("html", align = "lrrrr") |>
  kable_styling("striped", font_size = 12) |>
  add_header_above(c(" " = 1, "Antiviral" = 3, " " = 1))
```

```{r}
#| label: tbl-interventions-avs-itt
#| tbl-cap: Distribution of interventions assigned to participants, AVS-ITT.
#| cap-location: margin
tab <- make_intervention_table(all_data |> filter(ENR_rec == 1, AVS_ITT == 1))
savetab <- tab |>
  kable("latex", align = "lrrrr", booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 10) |>
  add_header_above(c(" " = 1, "Antiviral" = 2, " " = 1))
save_tex_table(
  savetab, 
  fn = file.path("baseline", "avs-itt-interventions")
)
tab |>
  kable("html", align = "lrrrr") |>
  kable_styling("striped", font_size = 12) |>
  add_header_above(c(" " = 1, "Antiviral" = 2, " " = 1))
```

```{r}
#| label: tbl-interventions-fas-pp
#| tbl-cap: Distribution of interventions assigned to participants, FAS-PP
#| cap-location: margin
tab <- make_intervention_table(fas_pp_dat)
savetab <- tab |>
  kable("latex", align = "lrrrr", booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 10) |>
  add_header_above(c(" " = 1, "Antiviral" = 3, " " = 1))
save_tex_table(
  savetab, 
  fn = file.path("baseline", "fas-pp-interventions")
)
tab |>
  kable("html", align = "lrrrr") |>
  kable_styling("striped", font_size = 12) |>
  add_header_above(c(" " = 1, "Antiviral" = 3, " " = 1))
```

```{r}
#| label: tbl-interventions-acs-pp
#| tbl-cap: Distribution of interventions assigned to participants, ACS-PP.
#| cap-location: margin
tab <- make_intervention_table(acs_pp_dat)
savetab <- tab |>
  kable("latex", align = "lrrrr", booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 10) |>
  add_header_above(c(" " = 1, "Antiviral" = 3, " " = 1))
save_tex_table(
  savetab, 
  fn = file.path("baseline", "acs-pp-interventions")
)
tab |>
  kable("html", align = "lrrrr") |>
  kable_styling("striped", font_size = 12) |>
  add_header_above(c(" " = 1, "Antiviral" = 3, " " = 1))
```

```{r}
#| label: tbl-interventions-avs-pp
#| tbl-cap: Distribution of interventions assigned to participants, AVS-PP.
#| cap-location: margin
tab <- make_intervention_table(avs_pp_dat)
savetab <- tab |>
  kable("latex", align = "lrrrr", booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 10) |>
  add_header_above(c(" " = 1, "Antiviral" = 2, " " = 1))
save_tex_table(
  savetab, 
  fn = file.path("baseline", "avs-pp-interventions")
)
tab |>
  kable("html", align = "lrrrr") |>
  kable_styling("striped", font_size = 12) |>
  add_header_above(c(" " = 1, "Antiviral" = 2, " " = 1))
```

## Country

Allocations to interventions by country of enrolment.

```{r}
#| label: tbl-allocation-country-anticoagulation
#| code-summary: Allocations by site
#| tbl-cap: |
#|   Allocation to anti-coagulation interventions by country.
all_data |>
  filter(ENR_rec == 1) |>
  dplyr::count(Country = PT_CountryName, Intervention = factor(CAssignment, labels = intervention_labels2()$CAssignment)) %>%
  group_by(Country) |>
  mutate(p = n / sum(n)) |>
  mutate(lab = sprintf("%i (%.2f)", n, p)) |>
  select(-n, -p) |>
  ungroup() |>
  spread(Intervention, lab, fill = "0 (0.00)") |>
  kable(align = "lrrrrr") %>%
  kable_styling(bootstrap_options = "striped", font_size = 10)
```

```{r}
#| label: tbl-allocation-country-antiviral
#| code-summary: Allocations by site
#| tbl-cap: |
#|   Allocation to anti-viral interventions by country.
all_data |>
  filter(ENR_rec == 1) |>
  dplyr::count(Country = PT_CountryName, Intervention = factor(AAssignment, labels = intervention_labels2()$AAssignment)) %>%
  group_by(Country) |>
  mutate(p = n / sum(n)) |>
  mutate(lab = sprintf("%i (%.2f)", n, p)) |>
  select(-n, -p) |>
  ungroup() |>
  spread(Intervention, lab, fill = "0 (0.00)") |>
  kable(align = "lrrrrr") %>%
  kable_styling(bootstrap_options = "striped", font_size = 10)
```

```{r}
#| label: fig-allocation-country-anticoagulation
#| code-summary: Allocations by country
#| fig-cap: |
#|   Allocation to anti-coagulation interventions by country.
#| fig-height: 4
p <- all_data |>
  filter(ENR_rec == 1) |>
  dplyr::count(Country = Country,
        Intervention = factor(CAssignment, labels = c("Not randomised", intervention_labels_short()$CAssignment[-1]))) %>%
  group_by(Country) |>
  mutate(p = n / sum(n)) |>
  ggplot(aes(Intervention, n)) +
  facet_wrap( ~ Country, scales = "free_y", ncol = 4) +
  geom_col() +
  scale_y_continuous("Frequency",
    breaks = function(x) 
      unique(floor(pretty(seq(0, (max(x) + 1) * 1.1))))) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.25))
pth <- file.path("outputs", "figures", "baseline")
ggsave(file.path(pth, "anticoagulation-allocations-country.pdf"), p, height = 2.5, width = 7)
p
```

```{r}
#| label: fig-allocation-country-antiviral
#| code-summary: Allocations by country
#| fig-cap: |
#|   Allocation to anti-viral interventions by country.
#| fig-height: 4
p <- all_data |>
  filter(ENR_rec == 1) |>
  dplyr::count(Country = Country,
        Intervention = factor(AAssignment, labels = c("Not randomised", intervention_labels_short()$AAssignment[-1]))) %>%
  group_by(Country) |>
  mutate(p = n / sum(n)) |>
  ggplot(aes(Intervention, n)) +
  facet_wrap( ~ Country, scales = "free_y", ncol = 4) +
  geom_col() +
  scale_y_continuous("Frequency",
    breaks = function(x) 
      unique(floor(pretty(seq(0, (max(x) + 1) * 1.1))))) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.25))
pth <- file.path("outputs", "figures", "baseline")
ggsave(file.path(pth, "antiviral-allocations-country.pdf"), p, height = 2.5, width = 7)
p
```

```{r}
#| label: fig-allocation-country-antiviral-noIndia
#| code-summary: Allocations by country
#| fig-cap: |
#|   Allocation to anti-viral interventions by country.
#| fig-height: 4
p <- all_data |>
  filter(ENR_rec == 1, Country != "IN", AAssignment != "A0") |>
  dplyr::count(
      Country = factor(Country, labels = c("Australia (AU)", "Nepal (NP)", "New Zealand (NZ)")),
      Intervention = factor(AAssignment, labels = intervention_labels_short()$AAssignment[-1])) %>%
  group_by(Country) |>
  mutate(p = n / sum(n)) |>
  ggplot(aes(Intervention, n)) +
  facet_wrap( ~ Country, scales = "free_y", ncol = 4) +
  geom_col() +
  scale_y_continuous("Frequency",
    breaks = function(x) 
      unique(floor(pretty(seq(0, (max(x) + 1) * 1.1)))))
pth <- file.path("outputs", "figures", "baseline")
fpth <- file.path(pth, "antiviral-allocations-country-no-india.pdf")
ggsave(fpth, p, height = 2.5, width = 7)
system(sprintf("pdftoppm %s %s -png", fpth, gsub(".pdf", "", fpth)))
p
```

## Site

Allocations to interventions by site of enrolment.

```{r}
#| label: fig-allocation-site-anticoagulation
#| code-summary: Allocations by site
#| fig-cap: |
#|   Allocation to anti-coagulation interventions by site
#| fig-height: 8
p <- all_data |>
  filter(ENR_rec == 1) |>
  dplyr::count(Country = Country, 
        Site = Location,
        Intervention = factor(CAssignment, labels = c("Not randomised", intervention_labels_short()$CAssignment[-1]))) %>%
  group_by(Site = paste(Country, Site, sep = ": ")) |>
  mutate(p = n / sum(n)) |>
  ggplot(aes(Intervention, n)) +
  facet_wrap( ~ Site, scales = "free_y") +
  geom_col() +
  scale_y_continuous("Frequency",
    breaks = function(x) 
      unique(floor(pretty(seq(0, (max(x) + 1) * 1.1))))) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.25))
pth <- file.path("outputs", "figures", "baseline")
ggsave(file.path(pth, "anticoagulation-allocations-sites.pdf"), p, height = 6, width = 7)
p
```

```{r}
#| label: fig-allocation-site-antiviral
#| code-summary: Allocations by site
#| fig-cap: |
#|   Allocation to anti-viral interventions by site
#| fig-height: 6
p <- all_data |>
  filter(ENR_rec == 1, Country != "IN") |>
  dplyr::count(Country = Country, 
        Site = Location,
        Intervention = factor(AAssignment, labels = c("Not randomised", intervention_labels_short()$AAssignment[-1]))) %>%
  group_by(Site = paste(Country, Site, sep = ": ")) |>
  mutate(p = n / sum(n)) |>
  ggplot(aes(Intervention, n)) +
  facet_wrap( ~ Site, scales = "free_y") +
  geom_col() +
  scale_y_continuous("Frequency",
    breaks = function(x) 
      unique(floor(pretty(seq(0, (max(x) + 1) * 1.1))))) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.25))
pth <- file.path("outputs", "figures", "baseline")
fpth <- file.path(pth, "antiviral-allocations-sites.pdf")
ggsave(fpth, p, height = 6, width = 7)
p
```


```{r}
#| label: fig-allocation-site-antiviral-noA0
#| code-summary: Allocations by site
#| fig-cap: |
#|   Allocation to anti-viral interventions by site
#| fig-height: 6
p <- all_data |>
  filter(ENR_rec == 1, Country != "IN", AAssignment != "A0") |>
  dplyr::count(Country = Country, 
        Site = Location,
        Intervention = factor(AAssignment, labels = intervention_labels_short()$AAssignment[-1])) %>%
  group_by(Site = paste(Country, Site, sep = ": ")) |>
  mutate(p = n / sum(n)) |>
  ggplot(aes(Intervention, n)) +
  facet_wrap( ~ Site, scales = "free_y") +
  geom_col() +
  scale_y_continuous("Frequency",
    breaks = function(x) 
      unique(floor(pretty(seq(0, (max(x) + 1) * 1.1))))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
pth <- file.path("outputs", "figures", "baseline")
fpth <- file.path(pth, "antiviral-allocations-sites-noA0.pdf")
ggsave(fpth, p, height = 6, width = 7)
system(sprintf("pdftoppm %s %s -png", fpth, gsub(".pdf", "", fpth)))
p
```

## Calender Time

```{r}
#| label: fig-allocation-epoch-anticoagulation
#| code-summary: Allocations by epoch
#| fig-cap: |
#|   Allocation to anti-coagulation interventions by country.
#| fig-height: 4
p <- all_data |>
  filter(ENR_rec == 1) |>
  dplyr::count(yr = year(RandDate), mth = month(RandDate),
        Intervention = factor(CAssignment, labels = c("Not randomised", intervention_labels_short()$CAssignment[-1]))) %>%
  group_by(yr, mth) |>
  mutate(p = n / sum(n)) |>
  ggplot(aes(mth, p, fill = Intervention)) +
  facet_grid( ~ yr, drop = T, scales = "free_x", space = "free") +
  geom_col() +
  scale_y_continuous("Distribution of\ninterventions") +
  scale_fill_viridis_d(option = "B")  +
    labs(
      x = "Calendar date (month of year)") +
  scale_x_continuous(breaks = 1:12)
pth <- file.path("outputs", "figures", "baseline")
ggsave(file.path(pth, "anticoagulation-allocations-calendar.pdf"), p, height = 2.5, width = 7)
p
```

```{r}
#| label: fig-allocation-epoch-anticoagulation2
#| code-summary: Allocations by epoch
#| fig-cap: |
#|   Allocation to anti-coagulation interventions by country.
#| fig-height: 4
p <- all_data |>
  filter(ENR_rec == 1) |>
  dplyr::count(yr = year(RandDate), mth = month(RandDate),
        Intervention = factor(CAssignment, labels = c("Not randomised", intervention_labels_short()$CAssignment[-1]))) %>%
  group_by(yr, mth) |>
  mutate(p = n / sum(n)) |>
  ggplot(aes(mth, n, fill = Intervention)) +
  facet_grid( ~ yr, drop = T, scales = "free_x", space = "free") +
  geom_col() +
  scale_y_continuous("Frequency of\ninterventions") +
  scale_fill_viridis_d(option = "B")  +
    labs(
      x = "Calendar date (month of year)") +
  scale_x_continuous(breaks = 1:12)
pth <- file.path("outputs", "figures", "baseline")
ggsave(file.path(pth, "anticoagulation-allocations-calendar2.pdf"), p, height = 2.5, width = 7)
p
```

```{r}
#| label: fig-allocation-epoch-antiviral
#| code-summary: Allocations by epoch
#| fig-cap: |
#|   Allocation to anti-viral interventions by country.
#| fig-height: 4
p <- all_data |>
  filter(ENR_rec == 1, Country != "IN") |>
  dplyr::count(yr = year(RandDate), mth = month(RandDate),
        Intervention = factor(AAssignment, labels = c("Not randomised", intervention_labels_short()$AAssignment[-1]))) %>%
  group_by(yr, mth) |>
  mutate(p = n / sum(n)) |>
  ggplot(aes(mth, p, fill = Intervention)) +
  facet_grid( ~ yr, drop = T, scales = "free_x", space = "free") +
  geom_col() +
  scale_y_continuous("Distribution of\ninterventions") +
  scale_fill_viridis_d(option = "B")  +
    labs(
      x = "Calendar date (month of year)") +
  scale_x_continuous(breaks = 1:12)
pth <- file.path("outputs", "figures", "baseline")
ggsave(file.path(pth, "antiviral-allocations-calendar.pdf"), p, height = 2.5, width = 7)
p
```

```{r}
#| label: fig-allocation-epoch-antiviral2
#| code-summary: Allocations by epoch
#| fig-cap: |
#|   Allocation to anti-viral interventions by country.
#| fig-height: 4
p <- all_data |>
  filter(ENR_rec == 1, Country != "IN") |>
  dplyr::count(yr = year(RandDate), mth = month(RandDate),
        Intervention = factor(AAssignment, labels = c("Not randomised", intervention_labels_short()$AAssignment[-1]))) %>%
  group_by(yr, mth) |>
  mutate(p = n / sum(n)) |>
  ggplot(aes(mth, n, fill = Intervention)) +
  facet_grid( ~ yr, drop = T, scales = "free_x", space = "free") +
  geom_col() +
  scale_y_continuous("Frequency of\ninterventions") +
  scale_fill_viridis_d(option = "B")  +
    labs(
      x = "Calendar date (month of year)") +
  scale_x_continuous(breaks = 1:12)
pth <- file.path("outputs", "figures", "baseline")
ggsave(file.path(pth, "antiviral-allocations-calendar2.pdf"), p, height = 2.5, width = 7)
p
```

# Baseline Factors

The following provides an overview of the baseline covariates collected for individuals who were enrolled and did not withdraw from follow-up.

## Demographics

Baseline demographics are summarised by intervention in the following table.

```{r}
#| label: demographics-table-setup
sdat <- all_data |>
    filter(ENR_rec == 1, WTH_FU == 0) |>
  mutate(
    AAssignment = factor(AAssignment, labels = c("A0", intervention_labels()$AAssignment[-1])),
    CAssignment = factor(CAssignment, labels = c("C0", intervention_labels()$CAssignment[-1]))
  )
sout <- generate_baseline_demographics_table(sdat, format = "html")
sout_latex <- generate_baseline_demographics_table(sdat, format = "latex")
```

```{r}
#| label: tbl-demographics-table-anticoagulation
#| code-summary: Demographics table
#| tbl-cap: |
#|   Baseline demographics for participants randomised into
#|   the anticoagulation domain.
save_tex_table(
  sout_latex[[2]],
  "baseline/demographics-anticoagulation"
)
sout[[2]]
```

```{r}
#| label: tbl-demographics-table-antiviral
#| code-summary: Demographics table
#| tbl-cap: |
#|   Baseline demographics for participants randomised into
#|   the antiviral domain.
save_tex_table(
  sout_latex[[1]],
  "baseline/demographics-antiviral"
)
sout[[1]]
```

## Co-morbidities

Baseline co-morbidities are summarised by anti-coagulation intervention in the following table.

```{r}
#| label: comorbidities-table-setup
sdat <- all_data |>
    filter(ENR_rec == 1, WTH_FU == 0) |>
  mutate(
    AAssignment = factor(AAssignment, labels = c("A0", intervention_labels()$AAssignment[-1])),
    CAssignment = factor(CAssignment, labels = c("C0", intervention_labels()$CAssignment[-1]))
  )
sout <- generate_baseline_comorbidities_table(sdat, format = "html")
sout_latex <- generate_baseline_comorbidities_table(sdat, format = "latex")
```

```{r}
#| label: tbl-comorbidities-table-anticoagulation
#| code-summary: Comorbidities table
#| tbl-cap: |
#|   Baseline comorbidities for participants randomised into
#|   the anticoagulation domain.
save_tex_table(
  sout_latex[[2]],
  "baseline/comorbidities-anticoagulation"
)
sout[[2]]
```

```{r}
#| label: tbl-comorbidities-table-antiviral
#| code-summary: Comorbidities table
#| tbl-cap: |
#|   Baseline comorbidities for participants randomised into
#|   the antiviral domain.
save_tex_table(
  sout_latex[[1]],
  "baseline/comorbidities-antiviral"
)
sout[[1]]
```

## Prognostics

Baseline prognostics are summarised by anti-coagulation intervention in the following table.

```{r}
#| label: prognostics-table-setup
sdat <- all_data |>
    filter(ENR_rec == 1, WTH_FU == 0) |>
  mutate(
    AAssignment = factor(AAssignment, labels = c("A0", intervention_labels()$AAssignment[-1])),
    CAssignment = factor(CAssignment, labels = c("C0", intervention_labels()$CAssignment[-1]))
  )
sout <- generate_baseline_prognostics_table(sdat, format = "html")
sout_latex <- generate_baseline_prognostics_table(sdat, format = "latex")
```

```{r}
#| label: tbl-prognostics-table-anticoagulation
#| code-summary: Prognostics table
#| tbl-cap: |
#|   Baseline prognostics for participants randomised into
#|   the anticoagulation domain.
save_tex_table(
  sout_latex[[2]],
  "baseline/prognostics-anticoagulation"
)
sout[[2]]
```

```{r}
#| label: tbl-prognostics-table-antiviral
#| code-summary: Prognostics table
#| tbl-cap: |
#|   Baseline prognostics for participants randomised into
#|   the antiviral domain.
save_tex_table(
  sout_latex[[1]],
  "baseline/prognostics-antiviral"
)
sout[[1]]
```

## Age

```{r}
#| label: fig-age-hist
#| code-summary: Histogram of age
#| fig-cap: |
#|   Distribution of age
#| fig-height: 2
p_age <- all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  ggplot(aes(AgeAtEntry)) + 
  geom_histogram(
    breaks = c(18, seq(20, 100, 5)), 
    colour = "white", 
    closed="left") +
  labs(
    x = "Age at randomisation (5-year bins, 30 to 34, 35 to 39, etc.)", 
    y = "Count") +
  scale_x_continuous(breaks = seq(20, 95, 5))
pth <- file.path("outputs", "figures", "baseline")
ggsave(file.path(pth, "age-overall.pdf"), p_age, height = 2, width = 4)
p_age
```

```{r}
#| label: fig-age-by-cassignment
#| code-summary: Histogram of age by anti-coagulation intervention
#| fig-cap: |
#|   Distribution of age by anti-coagulation intervention
#| fig-cap-location: bottom
#| fig-height: 4
p <- all_data |>
  filter(ENR_rec == 1, WTH_FU == 0, CAssignment != "C0") |>
  mutate(CAssignment = factor(CAssignment, labels = intervention_labels2()$CAssignment[-1])) |>
  ggplot(aes(AgeAtEntry)) + 
  facet_wrap( ~ CAssignment, scales = "free_y", ncol = 2) +
  geom_histogram(
    breaks = c(18, seq(20, 100, 5)), 
    colour = "white", 
    closed="left") +
  labs(
    x = "Age at randomisation (5-year bins, 30 to 34, 35 to 39, etc.)", 
    y = "Count") +
  scale_x_continuous(breaks = seq(20, 95, 5))
pth <- file.path("outputs", "figures", "baseline")
ggsave(file.path(pth, "age-domainc.pdf"), p, height = 4, width = 6)
p
```

```{r}
#| label: fig-age-by-aassignment
#| code-summary: Histogram of age by anti-viral intervention
#| fig-cap: |
#|   Distribution of age by anti-viral intervention.
#| fig-cap-location: bottom
#| fig-height: 3
p <- all_data |>
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  mutate(AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1])) |>
  ggplot(aes(AgeAtEntry)) + 
  facet_wrap( ~ AAssignment, scales = "free_y", ncol = 2) +
  geom_histogram(
    breaks = c(18, seq(20, 100, 5)), 
    colour = "white", 
    closed="left") +
  labs(
    x = "Age at randomisation (5-year bins, 30 to 34, 35 to 39, etc.)", 
    y = "Count") +
  scale_x_continuous(breaks = seq(20, 95, 5))
pth <- file.path("outputs", "figures", "baseline")
ggsave(file.path(pth, "age-domaina.pdf"), p, height = 2, width = 6)
p
```

## Weight

```{r}
#| label: fig-weight-hist
#| code-summary: Histogram of weight
#| fig-cap: |
#|   Distribution of weight
#| fig-height: 2
p <- all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  # 2 with weight reported as 0, make NA
  mutate(BAS_Weight = if_else(BAS_Weight == 0, NA_real_, BAS_Weight)) |>
  filter(!is.na(BAS_Weight)) |>
  ggplot(aes(BAS_Weight)) +
  facet_wrap( ~ BAS_WeightMeasurement, scales = "free_y") +
  geom_histogram(bins = 30) +
  labs(x = "Baseline weight (kg)", y = "Frequency")
p
```

```{r}
#| label: fig-weight-by-cassignment
#| code-summary: Histogram of weight by anti-coagulation intervention
#| fig-cap: |
#|   Distribution of weight by anti-coagulation intervention
#| fig-cap-location: bottom
#| fig-height: 3
p <- all_data |>
  filter(ENR_rec == 1, WTH_FU == 0, CAssignment != "C0") |>
  mutate(CAssignment = factor(CAssignment, labels = intervention_labels2()$CAssignment[-1])) |>
  mutate(BAS_Weight = if_else(BAS_Weight == 0, NA_real_, BAS_Weight)) |>
  filter(!is.na(BAS_Weight)) |>
  ggplot(aes(BAS_Weight)) + 
  facet_wrap( ~ CAssignment, scales = "free_y", ncol = 2) +
  geom_histogram(
    breaks = seq(40, 190, 5), 
    colour = "white", 
    closed="left") +
  scale_x_continuous("Baseline weight (kg)", breaks = seq(40, 190, 5)) +
  scale_y_continuous("Frequency",
  breaks = function(x) 
    unique(floor(pretty(seq(0, (max(x) + 1) * 1.1))))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```

```{r}
#| label: fig-weight-by-aassignment
#| code-summary: Histogram of weight by anti-viral intervention
#| fig-cap: |
#|   Distribution of weight by anti-viral intervention
#| fig-cap-location: bottom
#| fig-height: 2
p <- all_data |>
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  mutate(AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1])) |>
  mutate(BAS_Weight = if_else(BAS_Weight == 0, NA_real_, BAS_Weight)) |>
  filter(!is.na(BAS_Weight)) |>
  ggplot(aes(BAS_Weight)) + 
  facet_wrap( ~ AAssignment, ncol = 2) +
  geom_histogram(
    breaks = seq(40, 190, 5), 
    colour = "white", 
    closed="left") +
  scale_x_continuous("Baseline weight (kg)", breaks = seq(40, 190, 5)) +
  scale_y_continuous("Frequency",
  breaks = function(x) 
    unique(floor(pretty(seq(0, (max(x) + 1) * 1.1))))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```

## Date since first symptoms

```{r}
#| fig-cap: |
#|   Days between events for hospitalisation, randomisation,
#|   symptom onset, and first positive test.
#| fig-height: 4
tsfs_dat <- all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  transmute(
    CAssignment,
    RandDate,
    EL_AdmittedToHospital,
    EL_FirstSymptoms,
    EL_FirstPositiveTest,
    fs_to_hosp = as.numeric(EL_AdmittedToHospital - EL_FirstSymptoms),
    hosp_to_rand = as.numeric(RandDate - EL_AdmittedToHospital),
    fs_to_rand = as.numeric(RandDate - EL_FirstSymptoms),
    pt_to_rand = as.numeric(RandDate - EL_FirstPositiveTest))
p1 <- ggplot(tsfs_dat, aes(fs_to_hosp)) +
  geom_bar() +
  labs(x = "First symptoms to hospitalisation", 
       y = "Frequency")
p2 <- ggplot(tsfs_dat, aes(fs_to_rand)) +
  geom_bar() +
  labs(x = "First symptoms to randomisation", y = "Frequency")
p3 <- ggplot(tsfs_dat, aes(hosp_to_rand)) +
  geom_bar() +
  labs(x = "Hositalisation to randomisation", y = "Frequency")
p4 <- ggplot(tsfs_dat, aes(pt_to_rand)) +
  geom_bar() +
  labs(x = "Positive test to randomisation", y = "Frequency")
p <- (p1 | p2) / (p3 | p4)
pth <- file.path("outputs", "figures", "baseline")
ggsave(file.path(pth, "days-between-events-overall.pdf"), p, height = 3, width = 6)
p
```

## Oxygen Requirement

For supplemental oxygen requirement at baseline the relevant fields are:

- `BAS_OnRoomAir24hrs`
- `BAS_OnRoomAir24hrsUnknown`
- `BAS_PeripheralOxygen`

The logic is:

- if `BAS_OnRoomAir24hrs == "No"` then `supp_oxy = 1`
- if `BAS_OnRoomAir24hrs == "Yes" & BAS_PeripheralOxygen < 94` then `supp_oxy = 1`
- if `BAS_OnRoomAir24hrs == "Yes" & BAS_PeripheralOxygen >= 94` then `supp_oxy = 0`

There were 25 participants who had unknown supplemental oxygen status.
For the purpose of analysis, when this covariate is included, it is assumed that these participants *did not* require supplemental oxygen at baseline.

```{r}
Atab <- all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  count(
    Antiviral = factor(AAssignment, labels = intervention_labels()$AAssignment),
    `Supplemental oxygen at baseline` = supp_oxy) |>
  spread(Antiviral, n, fill = 0)
kable(Atab) |>
  kable_styling("striped", font_size = 12)

all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  count(
    Anticoagulation = factor(CAssignment, labels = intervention_labels()$CAssignment),
    `Supplemental oxygen at baseline` = supp_oxy) |>
  spread(Anticoagulation, n, fill = 0) |>
  kable() |>
  kable_styling("striped", font_size = 12)
```

## C-Reactive Protein

```{r}
#| label: fig-crp-hist
#| code-summary: Histogram of CRP
#| fig-cap: |
#|   Distribution of CRP
#| fig-height: 2
p <- all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  filter(!is.na(BAS_CRPResult)) |>
  ggplot(aes(BAS_CRPResult)) +
  facet_wrap( ~ BAS_CRPUnits , scales = "free_y") +
  geom_histogram(bins = 30) +
  labs(x = "CRP result (mg/L)", y = "Frequency")
p
```

It looks like there may be an issue with the conversion of CRP units or an issue with mis-specification of the reported units.

```{r}
all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  filter(!is.na(BAS_CRPResult)) |>
  ggplot(aes(BAS_CRPResult)) +
  stat_ecdf(aes(colour = BAS_CRPUnits)) + 
  facet_wrap( ~ Country) +
  labs(x = "CRP result (mg/L)", y = "Frequency") + 
  scale_x_log10()
```

```{r}
all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  filter(!is.na(BAS_CRPResult)) |>
  ggplot(aes(BAS_CRPEntered)) +
  stat_ecdf(aes(colour = BAS_CRPUnits)) + 
  facet_wrap( ~ Country) +
  labs(x = "CRP entered (mg/L or mg/dL)", y = "Frequency") + 
  scale_x_log10()
```

This was investigated with sites and corrections made to the reported units.

```{r}
all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  filter(!is.na(BAS_CRPResult_fixed)) |>
  ggplot(aes(BAS_CRPResult_fixed)) +
  stat_ecdf(aes(colour = BAS_CRPUnits)) + 
  facet_wrap( ~ Country) +
  labs(x = "Fixed CRP result (mg/L)", y = "Frequency") + 
  scale_x_log10()
```


```{r}
all_data |>
  filter(ENR_rec == 1, WTH_FU == 0, Country == "IN") |>
  filter(!is.na(BAS_CRPResult_fixed)) |>
  ggplot(aes(BAS_CRPResult_fixed)) +
  stat_ecdf(aes(colour = BAS_CRPUnits)) + 
  facet_wrap( ~ Location) +
  labs(x = "Fixed CRP result (mg/L)", y = "Frequency") + 
  scale_x_log10()
```

```{r}
all_data |>
  filter(ENR_rec == 1, WTH_FU == 0, Country == "IN") |>
  filter(!is.na(BAS_CRPResult)) |>
  ggplot(aes(BAS_CRPResult)) +
  stat_ecdf(aes(colour = BAS_CRPUnits)) + 
  facet_wrap( ~ Location) +
  labs(x = "Fixed CRP result (mg/L)", y = "Frequency") + 
  scale_x_log10()
```

# Drugs Received During Hospital Stay

```{r}
#| label: drugs-table-setup
sdat <- all_data |>
    filter(ENR_rec == 1, WTH_FU == 0) |>
  mutate(
    AAssignment = factor(AAssignment, labels = c("A0", intervention_labels()$AAssignment[-1])),
    CAssignment = factor(CAssignment, labels = c("C0", intervention_labels()$CAssignment[-1]))
  )
sout <- generate_discharge_drugs_table(sdat, format = "html")
sout_latex <- generate_discharge_drugs_table(sdat, format = "latex")
```

```{r}
#| label: tbl-drugs-table-anticoagulation
#| code-summary: Drugs table
#| tbl-cap: |
#|   Drugs received during hospital stay for participants randomised into
#|   the anticoagulation domain.
save_tex_table(
  sout_latex[[2]],
  "baseline/drugs-anticoagulation"
)
sout[[2]]
```

```{r}
#| label: tbl-drugs-table-antiviral
#| code-summary: Drugs table
#| tbl-cap: |
#|   Drugs received during hospital stay for participants randomised into
#|   the antiviral domain.
save_tex_table(
  sout_latex[[1]],
  "baseline/drugs-antiviral"
)
sout[[1]]
```

# Table 1

```{r}
generate_table_1(avs_itt_dat, "latex") |>
  save_tex_table("baseline/table-1")
generate_table_1(avs_itt_dat)
```
