---
title: "Patient Disposition"
description: |
  Summarise patient disposition throughout the trial,
  including eligibility, randomisation, and withdrawal.
author: "James Totterdell"
date: today
execute: 
  echo: false
  message: false
  warning: false
---

```{r}
#| label: pkgs
#| include: false
library(tidyverse)
library(kableExtra)
library(ASCOTr)
library(readxl)
```

```{r}
#| label: load-data
all_data <- readRDS(file.path(ASCOT_DATA, "all_data.rds"))
all_daily_data <- readRDS(file.path(ASCOT_DATA, "all_daily_data.rds"))

site_doma <- read_excel(file.path(ASCOT_DATA, "raw", "ListofSites_AVActivationDates.xlsx")) |>
  rename(date_doma = `First Activated onto Antiviral Domain`) |>
  select(Country, Site, date_doma)

el_doma <- all_data |> 
  select(StudyPatientID, ENR_rec, AAssignment, CAssignment, EL_LocationCode, starts_with("EL_")) |>
  left_join(site_doma, by = c("EL_LocationCode" = "Site")) |>
  left_join(
    all_data |> count(EL_LocationCode, EL_Country = PT_CountryName) |> filter(!is.na(EL_Country)),
    by = "EL_LocationCode"
  )
```

# Eligibility

## Platform Criteria

```{r}
#| label: tbl-platform-eligibility
#| tbl-cap: Platform eligibility.
all_data |>
  count(ENR_rec, EL_OutcomeReason) |>
  group_by(ENR_rec) |>
  arrange(-n, .by_group = TRUE) |>
  ungroup() |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

```{r}
#| label: tbl-consent-domainA
#| tbl-cap: Consent to domain A. One participant enrolled who did not consent.
all_data |>
  count(ENR_rec, EL_Con_DomainA) |>
  spread(EL_Con_DomainA, n) |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

```{r}
#| label: tbl-consent-domainC
#| tbl-cap: Consent to domain C.
all_data |>
  count(ENR_rec, EL_Con_DomainC) |>
  spread(EL_Con_DomainC, n) |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

## Antiviral Criteria

For reference, the exclusion criteria for the anti-viral domain follows (note that since only two antiviral interventions were available, an intervention exclusion criteria becomes a domain exclusion criteria):

- Known current decompensated liver disease (Child-Pugh B or C) (`EL_DecompensatedLiver`)
- The treating clinician intends to continue or commence treatment with oral therapeutic anticoagulation agents such as warfarin/dabigatran/rivaroxaban for non COVID-19 related purposes. (`EL_OralTherapeuticAnticoagAgents`)
- A current or recurrent condition with a high risk of major bleeding (e.g. bleeding disorder), or a baseline coagulation profile (within the previous 3 days) that indicates a high risk of bleeding, that would be considered a contraindication to receive therapeutic anticoagulation. (`EL_TherapeuticAnticoagBleeding`)
- Serum Potassium >5.5 mmol/L (based on most recent blood test result collected as part of routine care within the previous 3 days) (`EL_SerumPotassium`)
- Serum Sodium <120 mmol/L (based on most recent blood test result collected as part of routine care within the previous 3 days). (`EL_SerumSodium`)
- Hypersensitivity to nafamostat (`EL_HyperNafamostat`)
- Pregnancy or breastfeeding (`EL_PregnancyBreastfeedingStatus`)
- Currently receiving or have received nafamostat in the past 7 days (`EL_ReceivedNafamostat`)
- Decompensated heart failure or renal dialysis and clinician believes an extra 500mL fluid/day would be detrimental (`EL_HeartRenalDialysis`)

```{r}
#| label: tbl-antiviral-eligibility
#| tbl-cap: Antiviral eligibility variables.
all_data |>
    filter(
        ENR_rec == 1,
        EL_Con_DomainA == "Yes",
    ) |>
    summarise(
        EL_DecompensatedLiver = sum(EL_DecompensatedLiver == "Yes"),
        EL_OralTherapeuticAnticoagAgents = sum(EL_OralTherapeuticAnticoagAgents == "Yes", na.rm = TRUE),
        EL_TherapeuticAnticoagBleeding = sum(EL_TherapeuticAnticoagBleeding == "Yes"),
        EL_SerumSodium = sum(EL_SerumSodium < 5.5, na.rm = TRUE),
        EL_SerumPotassium = sum(EL_SerumPotassium >= 120, na.rm = TRUE),
        EL_HyperNafamostat = sum(EL_HyperNafamostat == "Yes"),
        EL_PregnancyBreastfeedingStatus = sum(EL_PregnancyBreastfeedingStatus == "Yes", na.rm = TRUE),
        EL_ReceivedNafamostat = sum(EL_ReceivedNafamostat == "Yes"),
        EL_HeartRenalDialysis = sum(EL_HeartRenalDialysis == "Yes")
    ) |>
    gather(Criteria, Count) |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

```{r}
#| label: tbl-antiviral-consent
#| tbl-cap: Antiviral ineligibility. Note that one participant
#|   was enrolled into the antiviral domain but did not actually consent.
#|   Antiviral specific outcomes set to missing for this participant.
all_data %>%
  filter(ENR_rec == 1) %>%
  dplyr::count(
    AAssignment,
    EL_Con_DomainA
  ) |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

```{r}
#| label: tbl-antiviral-primary-outcome
#| tbl-cap: Antiviral primary outcome.
all_data |>
  filter(ENR_rec == 1, AAssignment != "A0") |>
  count(AAssignment, PO) |>
  spread(PO, n) |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

## Anticoagulation Criteria

For reference, the exclusion criteria for the anti-coagulation domain follows (derived variable `EL_inelg_c`):

-  Receiving dual antiplatelet therapy (`EL_DualAntiplateletTherapy`)
-  The treating clinician intends to continue or commence therapeutic anticoagulation (`EL_TherapeuticAnticoag`)
-  Contraindication to receiving low molecular weight heparin or unfractionated heparin (`EL_ContraHeparinReact`)
-  Severe thrombocytopenia (platelet count less than 30 x $10^9$/L \[protocol version 3.0\] or less than 50 x $10^9$/L \[protocol version 5.0\] (`EL_BloodPlateletTestAs_x10_9_L`)
-  History of intracranial haemorrhage in the previous 3 months (`EL_IntracranialHaemorrhage`)
-  Severe renal impairment, defined as estimated glomerular filtration rate less than 15ml/min/1.73m$^2$ (`EL_eGFR`)
-  A current or recurrent condition with a high risk of major bleeding (e.g. bleeding disorder), or a baseline coagulation profile (within the previous 3 days) that indicates a high risk of bleeding, that would be considered a contraindication to receive therapeutic anticoagulation (`EL_BleedingConditionThrombo`)

```{r}
#| label: tbl-anticoagulation-consent
#| tbl-cap: Anticoagulation ineligibility.
all_data %>%
  filter(ENR_rec == 1) %>%
  dplyr::count(
    EL_inelg_c,
    CAssignment,
    EL_Con_DomainC
  ) |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

```{r}
#| label: tbl-anticoagulation-primary-outcome
#| tbl-cap: Anticoagulation primary outcome.
all_data |>
  filter(ENR_rec == 1, CAssignment != "C0") |>
  count(CAssignment, PO) |>
  spread(PO, n) |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

# Withdrawals

```{r}
#| label: tbl-withdrawal-summaries
#| tbl-cap: Withdrawals.
all_data |>
  count(
    WTH_FU, 
    CON_WithdrawnContact28, 
    CON_WithdrawnDailyCollection
) |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

```{r}
#| label: tbl-withdraw-reason
#| tbl-cap: Reason for patient withdrawals.
cntdat <- all_data |>
  count(
    WTH_FU, 
    CON_WithdrawnDomainA,
    CON_WithdrawnDomainC, 
    CON_WithdrawalReason, 
    CON_WithdrawalClincianReason
)
cntdat |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

```{r}
#| label: tbl-withdraw-count-domainA
#| tbl-cap: Withdrawals by domain A interventions.
all_data |>
  count(AAssignment, WTH_FU) |>
  spread(WTH_FU, n, fill = 0) |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

```{r}
#| label: tbl-withdraw-count-domainC
#| tbl-cap: Withdrawals by domain C interventions.
all_data |>
  count(WTH_FU, CAssignment) |>
  spread(WTH_FU, n, fill = 0) |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

# Other Summaries

```{r}
all_data |> 
  count(EL_LocationCode, Country) |> 
  spread(Country, n) |>
  print(n = Inf)

aa <- all_data |> 
  count(Country, Location, EL_LocationCode, AAssignment)

aaa <- aa |> 
  select(Country, Location) |> 
  distinct() |> 
  right_join(aa, by = c("Location" = "EL_LocationCode"))

aaa |>
  group_by(Country.x) |> 
  summarise(sum(n))

aa |> 
  filter(Country %in% c("AU", "NZ", "NP")) |> 
  group_by(Country) |> 
  summarise(sum(n))
aa |> 
  filter(is.na(Country)) |> 
  left_join(
    aa |> filter(!is.na(Country)), "EL_LocationCode") |> 
  group_by(Country.y) |> 
  summarise(sum(n.x))
```


# Update Flowchart

To make it clearer who was and wasn't enrolled into the antiviral domain want to update the flowchart to exclude those for whom it was unavailable.

```{r}
all_data |>
  filter(!is.na(EL_Con_DomainA)) |>
  count(ENR_rec, EL_Con_DomainA, EL_OutcomeReason, BAS_rec) |>
  print(n = Inf)
```

```{r}
all_data |>
  count(ENR_rec, EL_Con_DomainA, EL_OutcomeReason) |>
  print(n = Inf)
```


```{r}
all_data |>
  filter(!is.na(EL_HyperNafamostat)) |>
  count(ENR_rec, EL_OutcomeReason)
```

```{r}
all_data |>
  count(EL_HyperNafamostat)
```

```{r}
all_data |>
  count(EL_HyperNafamostat, EL_LocationCode) |>
  left_join(
    all_data |> count(EL_LocationCode, PT_CountryName) |> filter(!is.na(PT_CountryName)),
    by = "EL_LocationCode"
  ) |>
  group_by(EL_HyperNafamostat, PT_CountryName) |>
  summarise(sum(n.x))
```

```{r}
el_doma |> filter(EL_Country == "India") |> count(ENR_rec)
el_doma |> filter(EL_Country == "Australia") |> count(is.na(date_doma), EL_Screened >= date_doma, ENR_rec)
el_doma |> filter(EL_Country == "New Zealand") |> count(is.na(date_doma), EL_Screened >= date_doma, ENR_rec)
el_doma |> filter(EL_Country == "Nepal") |> count(is.na(date_doma), EL_Screened >= date_doma, ENR_rec)

el_doma |> count(ENR_rec, EL_Country)

el_doma |> 
  filter(EL_Country != "India", EL_Screened >= date_doma)  |>
  count(EL_HyperNafamostat, EL_OutcomeReason) |>
  group_by(EL_HyperNafamostat) |>
  arrange(-n, .by_group = T)

el_doma |> 
  filter(ENR_rec == 1, EL_Country != "India")  |>
  count(EL_Screened >= date_doma, EL_Con_DomainA)
el_doma |> 
  filter(ENR_rec == 1, EL_Country != "India")  |>
  count(EL_Con_DomainA)

el_doma |>
  count(ENR_rec, EL_OutcomeReason) |>
  arrange(-n, .by_group = T)

el_doma |>
  filter(ENR_rec == 1) |>
  count(EL_HyperNafamostat, EL_Screened >= date_doma, AAssignment)
  arrange(-n, .by_group = T)

 dd |> 
  filter(EL_Country == "Nepal") |>
  count(EL_Screened >= np_date, EL_HyperNafamostat, EL_OutcomeReason, AAssignment)

dd |> 
  filter(EL_Country == "New Zealand") |>
  count(EL_Screened >= aunz_date, EL_HyperNafamostat, EL_OutcomeReason, AAssignment)

dd |> 
  filter(EL_Country == "Australia") |>
  count(EL_Screened >= aunz_date, EL_HyperNafamostat, EL_OutcomeReason)
```

```{r}
#| label: tbl-platform-eligibility-antiviral
#| tbl-cap: Platform eligibility.
all_data |>
  filter(!is.na(EL_HyperNafamostat)) |>
  count(ENR_rec, EL_OutcomeReason) |>
  group_by(ENR_rec) |>
  arrange(-n, .by_group = TRUE) |>
  ungroup() |>
  kable("html") |>
  kable_styling("striped", font_size = 12)

all_data |>
  filter(!is.na(EL_HyperNafamostat)) |>
  count(ENR_rec, EL_OutcomeReason, EL_Con_DomainA, EL_Con_DomainC) |>
  group_by(ENR_rec) |>
  arrange(-n, .by_group = TRUE) |>
  ungroup() |>
  kable("html") |>
  kable_styling("striped", font_size = 12)

all_data |>
  filter(!is.na(EL_HyperNafamostat)) |>
  count(ENR_rec, EL_OutcomeReason, EL_Result) |>
  group_by(ENR_rec) |>
  arrange(-n, .by_group = TRUE) |>
  ungroup() |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```


```{r}
#| label: tbl-antiviral-eligibility
#| tbl-cap: Antiviral eligibility variables.
all_data |>
    filter(
        !is.na(EL_HyperNafamostat)
    ) |>
    group_by(ENR_rec) |>
    summarise(
        EL_DecompensatedLiver = sum(EL_DecompensatedLiver == "Yes"),
        EL_OralTherapeuticAnticoagAgents = sum(EL_OralTherapeuticAnticoagAgents == "Yes", na.rm = TRUE),
        EL_TherapeuticAnticoagBleeding = sum(EL_TherapeuticAnticoagBleeding == "Yes"),
        EL_SerumSodium = sum(EL_SerumSodium < 5.5, na.rm = TRUE),
        EL_SerumPotassium = sum(EL_SerumPotassium >= 120, na.rm = TRUE),
        EL_HyperNafamostat = sum(EL_HyperNafamostat == "Yes"),
        EL_PregnancyBreastfeedingStatus = sum(EL_PregnancyBreastfeedingStatus == "Yes", na.rm = TRUE),
        EL_ReceivedNafamostat = sum(EL_ReceivedNafamostat == "Yes"),
        EL_HeartRenalDialysis = sum(EL_HeartRenalDialysis == "Yes")
    ) |>
    gather(Criteria, Count, -ENR_rec) |>
  arrange(ENR_rec, Count) |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```

```{r}
#| label: tbl-antiviral-eligibility
#| tbl-cap: Antiviral eligibility variables.
all_data |>
    filter(
        is.na(EL_HyperNafamostat)
    ) |>
    group_by(ENR_rec) |>
    summarise(
        EL_DecompensatedLiver = sum(EL_DecompensatedLiver == "Yes", na.rm = TRUE),
        EL_OralTherapeuticAnticoagAgents = sum(EL_OralTherapeuticAnticoagAgents == "Yes", na.rm = TRUE),
        EL_TherapeuticAnticoagBleeding = sum(EL_TherapeuticAnticoagBleeding == "Yes", na.rm = TRUE),
        EL_SerumSodium = sum(EL_SerumSodium < 5.5, na.rm = TRUE, na.rm = TRUE),
        EL_SerumPotassium = sum(EL_SerumPotassium >= 120, na.rm = TRUE, na.rm = TRUE),
        EL_HyperNafamostat = sum(EL_HyperNafamostat == "Yes", na.rm = TRUE),
        EL_PregnancyBreastfeedingStatus = sum(EL_PregnancyBreastfeedingStatus == "Yes", na.rm = TRUE),
        EL_ReceivedNafamostat = sum(EL_ReceivedNafamostat == "Yes", na.rm = TRUE),
        EL_HeartRenalDialysis = sum(EL_HeartRenalDialysis == "Yes", na.rm = TRUE)
    ) |>
    gather(Criteria, Count, -ENR_rec) |>
  arrange(ENR_rec, Count) |>
  kable("html") |>
  kable_styling("striped", font_size = 12)
```
