---
title: "7-5 Days alive and free of invasive or non-invasive ventilation"
description: |
  This outcome was defined as the number of days alive and free of 
  invasive or non-invasive ventilation from randomisation to 28 days. 
  All patients dying within 28 days will be assigned zero free days.
author:
  - name: James Totterdell
    affiliation: University of Sydney
  - name: Rob Mahar
    affiliation: University of Melbourne
date: today
toc-depth: 5
freeze: true
---

```{r}
#| label: pkgs
#| code-summary: Load packages
library(ASCOTr)
library(tidyverse)
library(lubridate)
library(kableExtra)
library(patchwork)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(ggdist)
library(lme4)
library(broom)
library(broom.mixed)
library(bayestestR)

theme_set(theme_classic(base_size = 10, base_family = "Palatino") +
  theme(panel.grid = element_blank(),
        strip.background = element_blank()))

bayesplot_theme_set(theme_set(theme_classic(base_size = 10, base_family = "Palatino") +
  theme(panel.grid = element_blank(),
        strip.background = element_blank())))

color_scheme_set("red")
options(digits = 4)
```

```{r}
#| label: analysis-sets
#| code-summary: Prepare datasets
all_data <- readRDS(file.path(ASCOT_DATA, "all_data.rds"))

# FAS-ITT
fas_itt_dat <- ASCOTr:::make_fas_itt_set(all_data)
fas_itt_nona_dat <- fas_itt_dat |>
  filter(!is.na(out_dafv))

# ACS-ITT
acs_itt_dat <- ASCOTr:::make_acs_itt_set(all_data)
acs_itt_nona_dat <- acs_itt_dat |>
  filter(!is.na(out_dafv))

# AVS-ITT
avs_itt_dat <- ASCOTr:::make_avs_itt_set(all_data)
avs_itt_nona_dat <- avs_itt_dat |>
  filter(!is.na(out_dafv))
```

```{r}
#| label: models
#| code-summary: Load models
ordmod0 <- compile_cmdstanr_mod(
  file.path("ordinal", "logistic_cumulative"), dir = "stan")
ordmod <- compile_cmdstanr_mod(
  file.path("ordinal", "logistic_cumulative_epoch_site"), dir = "stan")
logistic <- compile_cmdstanr_mod(
  file.path("binary", "logistic_site_epoch"), dir = "stan")
```

```{r}
#| label: functions
#| code-summary: Functions
make_summary_table_anticoagulation <- function(dat, format = "html") {
  tdat <- dat %>%
    group_by(CAssignment = factor(
      CAssignment, 
      levels = c("C0", "C1", "C2", "C3", "C4"),
      labels = intervention_labels2()$CAssignment)) %>%
    summarise(
      Patients = n(),
      Known = sum(!is.na(out_dafv)),
      Deaths = sprintf("%i (%.0f%%)", sum(D28_death, na.rm = TRUE), 100 * mean(D28_death, na.rm = TRUE)),
      `Any ventilation` = sprintf("%i (%.0f%%)", 
                                  sum(D28_OutcomeDaysFreeOfVentilation < 28, na.rm = TRUE),
                                  100 * mean(D28_OutcomeDaysFreeOfVentilation < 28, na.rm = TRUE)),
      `DAFV, Median (Q1, Q3)` = sprintf(
        "%.0f (%.0f, %.0f)", 
        median(out_dafv, na.rm = T), 
        quantile(out_dafv, 0.25, na.rm = TRUE), 
        quantile(out_dafv, 0.75, na.rm = TRUE))
    ) %>%
    bind_rows(
      dat %>%
    group_by(CAssignment = "Overall") %>%
    summarise(
      Patients = n(),
      Known = sum(!is.na(out_dafv)),
      Deaths = sprintf("%i (%.0f%%)", sum(D28_death, na.rm = TRUE), 100 * mean(D28_death, na.rm = TRUE)),
      `Any ventilation` = sprintf("%i (%.0f%%)", 
                              sum(D28_OutcomeDaysFreeOfVentilation < 28, na.rm = TRUE),
                              100 * mean(D28_OutcomeDaysFreeOfVentilation < 28, na.rm = TRUE)),
      `DAFV, Median (Q1, Q3)` = sprintf(
        "%.0f (%.0f, %.0f)", 
        median(out_dafv, na.rm = T), 
        quantile(out_dafv, 0.25, na.rm = TRUE), 
        quantile(out_dafv, 0.75, na.rm = TRUE))
    )
    ) %>%
    rename(`Anticoagulation\nintervention` = CAssignment)
  kable(
    tdat,
    format = format,
    align = "lrrrrr",
    booktabs = TRUE,
    linesep = ""
  ) %>%
    kable_styling(
      font_size = 9,
      latex_options = "HOLD_position"
    ) %>%
    row_spec(nrow(tdat), bold = T)
}

make_summary_table_antiviral <- function(dat, format = "html") {
  tdat <- dat %>%
    group_by(AAssignment = factor(
      AAssignment, 
      levels = c("A0", "A1", "A2"),
      labels = intervention_labels2()$AAssignment)) %>%
    summarise(
      Patients = n(),
      Known = sum(!is.na(out_dafv)),
      Deaths = sprintf("%i (%.0f%%)", sum(D28_death, na.rm = TRUE), 100 * mean(D28_death, na.rm = TRUE)),
      `Any ventilation` = sprintf("%i (%.0f%%)", 
                                  sum(D28_OutcomeDaysFreeOfVentilation < 28, na.rm = TRUE),
                                  100 * mean(D28_OutcomeDaysFreeOfVentilation < 28, na.rm = TRUE)),
      `DAFV, Median (Q1, Q3)` = sprintf(
        "%.0f (%.0f, %.0f)", 
        median(out_dafv, na.rm = T), 
        quantile(out_dafv, 0.25, na.rm = TRUE), 
        quantile(out_dafv, 0.75, na.rm = TRUE))
    ) %>%
    bind_rows(
      dat %>%
    group_by(AAssignment = "Overall") %>%
    summarise(
      Patients = n(),
      Known = sum(!is.na(out_dafv)),
      Deaths = sprintf("%i (%.0f%%)", sum(D28_death, na.rm = TRUE), 100 * mean(D28_death, na.rm = TRUE)),
      `Any ventilation` = sprintf("%i (%.0f%%)", 
                              sum(D28_OutcomeDaysFreeOfVentilation < 28, na.rm = TRUE),
                              100 * mean(D28_OutcomeDaysFreeOfVentilation < 28, na.rm = TRUE)),
      `DAFV, Median (Q1, Q3)` = sprintf(
        "%.0f (%.0f, %.0f)", 
        median(out_dafv, na.rm = T), 
        quantile(out_dafv, 0.25, na.rm = TRUE), 
        quantile(out_dafv, 0.75, na.rm = TRUE))
    )
    ) %>%
    rename(`Antiviral\nintervention` = AAssignment)
  kable(
    tdat,
    format = format,
    align = "lrrrrr",
    booktabs = TRUE,
    linesep = ""
  ) %>%
    kable_styling(
      font_size = 9,
      latex_options = "HOLD_position"
    ) %>%
    row_spec(nrow(tdat), bold = T)
}
```

# Outcome Derivation

This outcome was defined as the number of days alive and free of positive pressure ventilation
(invasive or non-invasive) to 28 days. All patients dying within 28 days will be assigned zero free days.

The outcome is calculated for a patient as:

- missing, if day 28 mortality is unknown (`D28_PatientStatus`) or if the patient was known to have been alive
  at day 28 but number of days requiring ventilation (`D28_OutcomeDaysFreeOfVentilation`) is unknown
- 0 if they died by day 28 (`D28_PatientStatus`)
- `min(28, D28_OutcomeDaysFreeOfVentilation)` otherwise

# Descriptive {#descriptive}

The overall distribution of days alive and free of ventilation (DAFV) are reported in @fig-dafv-dist for all participants in the ACS-ITT set.

There were few participants who required any ventilation during hospital who did not die (DAFV of 0),

```{r}
#| label: fig-dafv-dist
#| fig-cap: |
#|   Distribution of days alive and free of ventilation
#| fig-subcap: FAS-ITT
#| fig-height: 4
pdat <- fas_itt_nona_dat %>%
  dplyr::count(dafv = ordered(out_dafv, levels = 0:28), .drop = F) %>%
  mutate(p = n / sum(n))
p <- ggplot(pdat, aes(dafv, p)) +
  geom_col() +
  labs(
    x = "Days alive and free of ventilation", 
    y = "Proportion"
  )
path <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(path, "outcome-7-5-dist-overall.pdf"), p, height = 2.5, width = 6)
p
```

## Anticoagulation

```{r}
#| label: tbl-7-5-summary-anticoagulation
#| code-summary: Summary of DAFH outcome by arm
#| tbl-cap: Summary of days alive and free of ventilation to day 28 by anticoagulation treatment group, FAS-ITT.
save_tex_table(
  make_summary_table_anticoagulation(fas_itt_dat, "latex"), 
  file.path("outcomes", "secondary", "7-5-anticoagulation-summary"))
make_summary_table_anticoagulation(fas_itt_dat)
```

```{r}
#| label: fig-dafh-dist-anticoagulation
#| fig-cap: |
#|   Distribution of days alive and free of hospital by anti-coagulation intervention.
#| fig-height: 4
pdat <- fas_itt_nona_dat %>%
  dplyr::count(
    CAssignment = factor(CAssignment, labels = str_replace(intervention_labels()$CAssignment, "<br>", "\n")),
    dafv = ordered(out_dafv, levels = 0:28), 
    .drop = F) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup()
p <- ggplot(pdat, aes(CAssignment, p)) +
  geom_col(aes(fill = fct_rev(dafv))) +
  labs(x = "Anticoagulation intervention", y = "Cumulative proportion") +
  scale_fill_viridis_d("Days alive and\nfree of ventilation", option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = TRUE)) +
  theme(legend.key.size = unit(0.75, "lines"))
pth <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(pth, "outcome-7-5-descriptive-anticoagulation.pdf"), p, height = 3, width = 6)
p
```

```{r}
#| label: fig-dafh-dist-anticoagulation-avs-itt
#| fig-cap: |
#|   Distribution of days alive and free of hospital by anti-coagulation intervention.
#| fig-height: 4
pdat <- avs_itt_nona_dat %>%
  dplyr::count(
    CAssignment = factor(CAssignment, labels = str_replace(intervention_labels()$CAssignment, "<br>", "\n")),
    dafv = ordered(out_dafv, levels = 0:28), 
    .drop = F) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup()
p <- ggplot(pdat, aes(CAssignment, p)) +
  geom_col(aes(fill = fct_rev(dafv))) +
  labs(x = "Anticoagulation intervention", y = "Cumulative proportion") +
  scale_fill_viridis_d("Days alive and\nfree of ventilation", option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = TRUE)) +
  theme(legend.key.size = unit(0.75, "lines"))
pth <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(pth, "outcome-7-5-descriptive-anticoagulation-avs-itt.pdf"), p, height = 3, width = 6)
p
```

## Antiviral

```{r}
#| label: tbl-7-5-summary-antiviral
#| code-summary: Summary of DAFH outcome by arm
#| tbl-cap: Summary of days alive and free of ventilation to day 28 by antiviral treatment group, FAS-ITT.
save_tex_table(
  make_summary_table_antiviral(fas_itt_dat, "latex"), 
  file.path("outcomes", "secondary", "7-5-antiviral-summary"))
make_summary_table_antiviral(fas_itt_dat)
```

```{r}
#| label: fig-dafh-dist-antiviral
#| fig-cap: |
#|   Distribution of days alive and free of hospital by antiviral intervention.
#| fig-height: 4
pdat <- fas_itt_nona_dat %>%
  dplyr::count(
    AAssignment = factor(AAssignment, labels = str_replace(intervention_labels()$AAssignment, "<br>", "\n")),
    dafv = ordered(out_dafv, levels = 0:28), 
    .drop = F) %>%
  group_by(AAssignment) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup()
p <- ggplot(pdat, aes(AAssignment, p)) +
  geom_col(aes(fill = fct_rev(dafv))) +
  labs(x = "Antiviral intervention", y = "Cumulative proportion") +
  scale_fill_viridis_d("Days alive and\nfree of ventilation", option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = TRUE)) +
  theme(legend.key.size = unit(0.75, "lines"))
pth <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(pth, "outcome-7-5-descriptive-antiviral.pdf"), p, height = 3, width = 6)
p
```

```{r}
#| label: fig-dafh-dist-antiviral-acs-itt
#| fig-cap: |
#|   Distribution of days alive and free of hospital by antiviral intervention.
#| fig-height: 4
pdat <- acs_itt_nona_dat %>%
  dplyr::count(
    AAssignment = factor(AAssignment, labels = str_replace(intervention_labels()$AAssignment, "<br>", "\n")),
    dafv = ordered(out_dafv, levels = 0:28), 
    .drop = F) %>%
  group_by(AAssignment) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup()
p <- ggplot(pdat, aes(AAssignment, p)) +
  geom_col(aes(fill = fct_rev(dafv))) +
  labs(x = "Antiviral intervention", y = "Cumulative proportion") +
  scale_fill_viridis_d("Days alive and\nfree of ventilation", option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = TRUE)) +
  theme(legend.key.size = unit(0.75, "lines"))
pth <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(pth, "outcome-7-5-descriptive-antiviral-acs-itt.pdf"), p, height = 3, width = 6)
p
```

## Age

```{r}
#| label: fig-dafv-dist-age
#| code-summary: DAFV by age
#| fig-cap: |
#|   Distribution of days alive and free of ventilation by age group, FAS-ITT.
#| fig-height: 4
pdat <- fas_itt_nona_dat %>%
  dplyr::count(
    agegrp = cut(AgeAtEntry, c(18, seq(25, 75, 5), 100), include.lowest = T, right = F),
    dafv = fct_rev(ordered(out_dafv, levels = 0:28)), 
    .drop = F) %>%
  group_by(agegrp) %>%
  mutate(p = n / sum(n))
pdat2 <- pdat %>%
  group_by(agegrp) %>%
  summarise(n = sum(n))
p1 <- ggplot(pdat2, aes(agegrp, n)) +
  geom_col(colour = "grey40", fill = "grey40") +
  geom_vline(xintercept = 60, linetype = 2) +
  labs(y = "Number of\nparticipants",
       x = "Age at entry") +
  geom_vline(xintercept = 8.5, linetype = 2) +
  theme(axis.text.x = element_text(hjust = 1, angle = 45))
p2 <- ggplot(pdat, aes(agegrp, p)) +
  geom_col(aes(fill = dafv)) +
  labs(x = "Age", y = "Cumulative\nproportion") +
  scale_fill_viridis_d("DAFV", option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = TRUE)) +
  geom_vline(xintercept = 8.5, linetype = 2) +
  theme(axis.text.x = element_text(hjust = 1, angle = 45)) +
  theme(legend.key.size = unit(0.25, "lines"))
p <- p1 | p2
path <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(path, "7-5-age.pdf"), p, height = 2.5, width = 6)
p
```

## Country

```{r}
#| label: fig-dafv-dist-country
#| code-summary: DAFV by country
#| fig-cap: |
#|   Distribution of days alive and free of ventilation by country.
#| fig-height: 4
pdat <- fas_itt_nona_dat %>%
  dplyr::count(
    Country = fct_infreq(Country),
    dafv = ordered(out_dafv, levels = 0:28), 
    .drop = F) %>%
  group_by(Country) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup()
pdat2 <- pdat %>%
  group_by(Country) %>%
  summarise(n = sum(n))
p1 <- ggplot(pdat2, aes(Country, n)) +
  geom_col() +
    labs(
      y = "Number of\nparticipants", 
      x = "Country of enrolment")
p2 <- ggplot(pdat, aes(Country, p)) +
  geom_col(aes(fill = fct_rev(dafv))) +
  labs(x = "Anticoagulation intervention", y = "Cumulative\nproportion") +
  scale_fill_viridis_d("DAFV", option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = TRUE)) +
  theme(legend.key.size = unit(0.25, "lines"))
p <- p1 | p2
path <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(path, "7-5-country.pdf"), p, height = 2.5, width = 6)
p
```

## Site

```{r}
#| label: fig-dafv-dist-site
#| code-summary: DAFV by site
#| fig-cap: |
#|   Distribution of days alive and free of ventilation by study site
#| fig-height: 4
pdat <- fas_itt_nona_dat %>%
  dplyr::count(
    Country = factor(PT_CountryName, levels = c("India", "Australia", "Nepal", "New Zealand"),
                     labels = c("India", "Australia", "Nepal", "New\nZealand")),
    Site = fct_infreq(Location),
    dafv = ordered(out_dafv, levels = 0:28)) %>%
  complete(dafv = ordered(0:28), nesting(Country, Site), fill = list(n = 0)) %>%
  group_by(Country, Site) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup() %>%
  mutate(
    Country = droplevels(Country),
    Site = droplevels(Site)
  )
pdat2 <- pdat %>%
  group_by(Country, Site) %>%
  summarise(n = sum(n)) %>%
  ungroup()
p1 <- ggplot(pdat2, aes(Site, n)) +
  facet_grid( ~ Country, scales = "free_x", space = "free_x") +
  geom_col() +
    labs(
      y = "Number of\nparticipants", 
      x = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.border = element_rect(fill = NA))
p2 <- ggplot(pdat, aes(Site, p)) +
  facet_grid( ~ Country, scales = "free_x", space = "free_x") +
  geom_col(aes(fill = fct_rev(dafv))) +
  labs(x = "Anticoagulation intervention", y = "Cumulative\nproportion") +
  scale_fill_viridis_d("DAFV", option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = TRUE, ncol = 1)) +
  theme(axis.text.x = element_text(hjust = 1, angle = 45)) +
  theme(legend.key.size = unit(0.25, "lines"))
p <- p1 / p2 +
  plot_layout(guides = 'collect')
path <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(path, "7-5-country-site.pdf"), p, height = 4, width = 6.25)
p
```

## Calendar Time

```{r}
#| label: fig-dafv-dist-calendar
#| code-summary: DAFV by calendar date
#| fig-cap: |
#|   Distribution of days alive and free of ventilation by calendar time.
#| fig-height: 4
pdat <- fas_itt_nona_dat %>%
  dplyr::count(
    yr = year(RandDate), mth = month(RandDate),
    dafv = ordered(out_dafv, levels = 0:28), 
    .drop = F) %>%
  group_by(yr, mth) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup()
p1 <- pdat %>%
  group_by(yr, mth) %>%
  summarise(n = sum(n)) %>%
  ggplot(., aes(mth, n))  +
  facet_grid( ~ yr, drop = T, scales = "free_x", space = "free") +
    geom_col() +
    labs(
      y = "Number of\nparticipants", 
      x = "Calendar date (month of year)") +
  scale_x_continuous(breaks = 1:12)
p2 <- ggplot(pdat, aes(mth, p)) +
  facet_grid( ~ yr, drop = T, scales = "free_x", space = "free") +
  geom_col(aes(fill = fct_rev(dafv))) +
  labs(x = "Calendar date (month of year)", y = "Cumulative\nproportion") +
  scale_fill_viridis_d("DAFV", option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = TRUE)) +
  theme(legend.key.size = unit(0.25, "lines")) +
  scale_x_continuous(breaks = 1:12)
p <- p1 | p2
path <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(path, "7-5-calendar-time.pdf"), p, height = 2, width = 6)
p
```

## Sample Cumulative Logits

```{r}
#| code-summary: Plot sample cumulative logits
#| fig-cap: Inspect sample cumulative logits.
trt_counts <- fas_itt_nona_dat %>%
  dplyr::count(CAssignment, out_dafv) %>%
  complete(CAssignment, out_dafv, fill = list(n = 0)) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n))
trt_logit <- trt_counts %>% 
  group_by(CAssignment) %>% 
  mutate(clogit = logit(cumsum(p))) %>%
  group_by(out_dafv) %>%
  mutate(rel_clogit = clogit - mean(clogit)) %>%
  filter(out_dafv != 28)
ggplot(trt_logit, aes(CAssignment, rel_clogit)) +
  facet_wrap( ~ out_dafv) +
  geom_point() +
  labs(y = "Relative (to mean) sample cumulative logit")
ggplot(trt_logit, aes(out_dafv, rel_clogit)) +
  facet_wrap( ~ CAssignment) +
  geom_point() +
  labs(y = "Relative (to mean) sample cumulative logit")
```

```{r}
#| code-summary: Plot sample cumulative logits
#| fig-cap: Inspect sample cumulative logits.
trt_counts <- fas_itt_nona_dat %>%
  dplyr::count(AAssignment, out_dafv) %>%
  complete(AAssignment, out_dafv, fill = list(n = 0)) %>%
  group_by(AAssignment) %>%
  mutate(p = n / sum(n))
trt_logit <- trt_counts %>% 
  group_by(AAssignment) %>% 
  mutate(clogit = logit(cumsum(p))) %>%
  group_by(out_dafv) %>%
  mutate(rel_clogit = clogit - mean(clogit)) %>%
  filter(out_dafv != 28)
ggplot(trt_logit, aes(AAssignment, rel_clogit)) +
  facet_wrap( ~ out_dafv) +
  geom_point() +
  labs(y = "Relative (to mean) sample cumulative logit")
ggplot(trt_logit, aes(out_dafv, rel_clogit)) +
  facet_wrap( ~ AAssignment) +
  geom_point() +
  labs(y = "Relative (to mean) sample cumulative logit")
```

# Modelling

## FAS-ITT

```{r}
#| label: fit-model-fas-itt
#| code-summary: Fit primary model
res <- fit_primary_model(
  fas_itt_nona_dat,
  ordmod,
  outcome = "out_dafv",
  intercept = FALSE
)
names(res$drws$AOR) <- "Nafamostat"
names(res$drws$COR) <- intervention_labels2()$CAssignment[-(1:2)]
names(res$drws$OR) <- c("Ineligible aspirin", "Age \u2265 60", "Oxygen requirement", "Australia/New Zealand", "Nepal")
```

```{r}
#| label: odds-ratio-summary-table-primary-model-save-fas-itt
#| code-summary: Odds ratio summary table
#| tbl-cap: Posterior summaries for model parameters (fixed-effects).
save_tex_table(
  odds_ratio_summary_table_rev(c(res$drws$AOR, res$drws$COR, res$drws$OR), "latex"),
  "outcomes/secondary/7-5-primary-model-fas-itt-summary-table")
odds_ratio_summary_table_rev(c(res$drws$AOR, res$drws$COR, res$drws$OR))
```

```{r}
#| label: fig-or-densities-fas-itt-model
#| fig-cap: Posterior densities for odds ratio contrasts.
p <- plot_or_densities(c(res$drws$AOR, res$drws$COR)) +
  labs(x = "Odds ratio (log scale)", y = "Comparison")
pth <- file.path("outputs", "figures", "outcomes", "primary", "7-5-primary-model-fas-itt-odds-ratio-densities.pdf")
ggsave(pth, p, width = 6, height = 2.5)
p
```

```{r}
#| code-summary: Odds ratio summary for epoch and site
#| fig-cap: Summary of epoch and site posterior odds ratios.
p <- plot_epoch_site_terms(
  res$drws$gamma_epoch,
  res$drws$gamma_site,
  factor(res$dat$region_by_site, 
         labels = c("India", "Australia\nNew Zealand", "Nepal"))
)
pth <- file.path("outputs", "figures", "outcomes", "secondary", "7-5-primary-model-fas-itt-epoch-site-terms.pdf")
ggsave(pth, p, width = 6, height = 4.5)
p
```

:::{.callout-caution collapse="true"}
###### Diagnostics
```{r}
res$fit$summary(c("alpha", "beta", "gamma_site", "gamma_epoch", "tau_site", "tau_epoch")) %>%
  print(n = Inf)
res$fit$diagnostic_summary()
```
:::

:::{.callout-caution collapse="true"}
###### Trace plots
```{r}
mcmc_trace(res$drws["beta"])
mcmc_trace(res$drws["alpha"])
mcmc_trace(res$drws["gamma_site"])
mcmc_trace(res$drws["gamma_epoch"])
```
:::

### Posterior Predictive

```{r}
y_raw <- as.integer(levels(res$dat$y_raw))
y_ppc <- res$drws$y_ppc
y_ppc_raw <- rfun(\(x) y_raw[x])(y_ppc)
ppc_dat <- bind_cols(fas_itt_nona_dat, tibble(y_ppc = y_ppc_raw))
grp_ppc <- function(grp, d = 0:27) {
  ppc_dat %>%
    group_by(grp = {{grp}}) %>%
    summarise(
      y_lteq = map_dbl(d, ~ mean(out_dafv <= .x)),
      ypp_lteq = map(d, ~ rvar_mean(y_ppc <= .x)),
      y_eq = map_dbl(d, ~ mean(out_dafv == .x)),
      ypp_eq = map(d, ~ rvar_mean(y_ppc == .x))
    ) %>%
    unnest(c(ypp_lteq, ypp_eq)) %>%
    mutate(days = d) %>%
    ungroup() %>%
    pivot_longer(
      y_lteq:ypp_eq, 
      names_to = c("response", "event"),
      names_sep = "_",
      values_to = "posterior")
}
plot_grp_ppc <- function(dat, lab = "", xlab = "Probability") {
  ggplot(dat %>% 
           filter(response == "ypp", event == "eq"), 
         aes(y = days)) +
    facet_wrap( ~ grp, nrow = 1, scales = "free_x") +
    stat_slabinterval(aes(xdist = posterior), fatten_point = 1)  +
    geom_point(data = dat %>% filter(response == "y", event == "eq"), 
               aes(y = days, x = mean(posterior)),
               colour = "red",
               shape = 23) +
    scale_x_continuous(
      xlab, breaks = c(0, 0.3, 0.6),
      sec.axis = sec_axis(
        ~ . , name = lab, breaks = NULL, labels = NULL)) +
    scale_y_continuous("Days") +
    theme(strip.text = element_text(size = rel(0.7)),
          axis.title.x = element_text(size = rel(0.7)),
          axis.text.x = element_text(size = rel(0.65)),
          axis.title.y = element_text(size = rel(0.75)),
          axis.title.x.bottom = element_blank())
}
pp_A <- grp_ppc(AAssignment)
pp_C <- grp_ppc(CAssignment)
pp_ctry <- grp_ppc(Country)
pp_epoch <- grp_ppc(epoch)
pp_site <- grp_ppc(site) %>%
  left_join(ppc_dat %>% dplyr::count(site, Country), 
            by = c("grp" = "site"))
p0 <- plot_grp_ppc(pp_A, "Antiviral", "")
p1 <- plot_grp_ppc(pp_C, "Anticoagulation", "")
p2 <- plot_grp_ppc(pp_ctry, "Country", "") 
p3 <- plot_grp_ppc(pp_epoch, "Epoch", "")
p4 <- plot_grp_ppc(
  pp_site %>% filter(Country == "IN"), "Sites India", "")
p5 <- plot_grp_ppc(
  pp_site %>% filter(Country == "AU"), "Sites Australia", "")
p6 <- plot_grp_ppc(
  pp_site %>% filter(Country == "NP"), "Sites Nepal", "")
p7 <- plot_grp_ppc(
  pp_site %>% filter(Country == "NZ"), "Sites New Zealand", "")
g1 <- (p0 | p1 | p2) / p3
g2 <- p4 / p5 / (p6 | p7)
pth1 <- file.path(
  "outputs", "figures", "outcomes", "secondary",
  "7-5-primary-model-fas-itt-ppc1.pdf")
pth2 <- file.path(
  "outputs", "figures", "outcomes", "secondary",
  "7-5-primary-model-fas-itt-ppc2.pdf")
ggsave(pth1, g1, width = 6, height = 5, device = cairo_pdf)
ggsave(pth2, g2, width = 6, height = 6, device = cairo_pdf)
g1
g2
```

## ACS-ITT

```{r}
#| label: fit-model-acs-itt
#| code-summary: Fit primary model
res <- fit_primary_model(
  acs_itt_nona_dat,
  ordmod,
  outcome = "out_dafv",
  intercept = FALSE
)
names(res$drws$AOR) <- "Nafamostat"
names(res$drws$COR) <- intervention_labels2()$CAssignment[-(1:2)]
names(res$drws$OR) <- c("Ineligible aspirin", "Age \u2265 60", "Oxygen requirement", "Australia/New Zealand", "Nepal")
```

```{r}
#| label: odds-ratio-summary-table-primary-model-save-acs-itt
#| code-summary: Odds ratio summary table
#| tbl-cap: Posterior summaries for model parameters (fixed-effects).
save_tex_table(
  odds_ratio_summary_table_rev(c(res$drws$AOR, res$drws$COR, res$drws$OR), "latex"),
  "outcomes/secondary/7-5-primary-model-acs-itt-summary-table")
odds_ratio_summary_table_rev(c(res$drws$AOR, res$drws$COR, res$drws$OR))
```

```{r}
#| label: fig-or-densities-acs-itt-model
#| fig-cap: Posterior densities for odds ratio contrasts.
p <- plot_or_densities(c(res$drws$AOR, res$drws$COR)) +
  labs(x = "Odds ratio (log scale)", y = "Comparison")
pth <- file.path("outputs", "figures", "outcomes", "primary", "7-5-primary-model-acs-itt-odds-ratio-densities.pdf")
ggsave(pth, p, width = 6, height = 2.5)
p
```

```{r}
#| code-summary: Odds ratio summary for epoch and site
#| fig-cap: Summary of epoch and site posterior odds ratios.
p <- plot_epoch_site_terms(
  exp(res$drws$gamma_epoch),
  exp(res$drws$gamma_site),
  factor(res$dat$region_by_site, 
         labels = c("India", "Australia\nNew Zealand", "Nepal"))
)
pth <- file.path("outputs", "figures", "outcomes", "secondary", "7-5-primary-model-acs-itt-epoch-site-terms.pdf")
ggsave(pth, p, width = 6, height = 4.5)
p
```

## AVS-ITT

### Pre-specified

```{r}
#| label: fit-model-avs-itt
#| code-summary: Fit primary model
res <- fit_primary_model(
  fas_itt_nona_dat,
  ordmod,
  outcome = "out_dafv",
  vars = c("agegte60", "supp_oxy2"),
  beta_sd_var = c(2.5, 2.5),
  intercept = FALSE
)
names(res$drws$AOR) <- "Nafamostat"
names(res$drws$COR) <- intervention_labels2()$CAssignment[-(1:2)]
names(res$drws$OR) <- c("Age \u2265 60", "Oxygen requirement")
```

```{r}
#| label: odds-ratio-summary-table-primary-model-save-avs-itt
#| code-summary: Odds ratio summary table
#| tbl-cap: Posterior summaries for model parameters (fixed-effects), AVS-ITT.
save_tex_table(
  odds_ratio_summary_table_rev(c(res$drws$AOR, res$drws$COR, res$drws$OR), "latex"),
  "outcomes/secondary/7-5-primary-model-avs-itt-summary-table")
odds_ratio_summary_table_rev(c(res$drws$AOR, res$drws$COR, res$drws$OR))
```

```{r}
#| label: fig-or-densities-avs-itt-model
#| fig-cap: Posterior densities for odds ratio contrasts, AVS-ITT.
p <- plot_or_densities(c(res$drws$AOR, res$drws$COR)) +
  labs(x = "Odds ratio (log scale)", y = "Comparison")
pth <- file.path("outputs", "figures", "outcomes", "primary", "7-5-primary-model-avs-itt-odds-ratio-densities.pdf")
ggsave(pth, p, width = 6, height = 2.5)
p
```

### Treatment Only

```{r}
res <- fit_primary_model(
  avs_itt_nona_dat,
  ordmod0,
  outcome = "out_dafv",
  vars = NULL,
  beta_sd_var = NULL,
  intercept = FALSE
)
names(res$drws$AOR) <- "Nafamostat"
```

```{r}
#| label: odds-ratio-summary-table-avs-itt-trt-only
#| code-summary: Odds ratio summary table
#| tbl-cap: Posterior summaries for model parameters (fixed-effects), AVS-ITT.
save_tex_table(
  odds_ratio_summary_table_rev(c(res$drws$AOR), "latex"),
  "outcomes/secondary/7-5-primary-model-avs-itt-summary-table-trt-only")
odds_ratio_summary_table_rev(c(res$drws$AOR))
```

```{r}
#| label: fig-or-densities-avs-itt-model-trt-only
#| fig-cap: Posterior densities for odds ratio contrasts.
p <- plot_or_densities(c(res$drws$AOR)) +
  labs(x = "Odds ratio (log scale)", y = "Comparison")
pth <- file.path("outputs", "figures", "outcomes", "primary", "7-5-primary-model-avs-itt-odds-ratio-densities-trt-only.pdf")
ggsave(pth, p, width = 6, height = 2.5)
p
```
