---
title: "8 - Antiviral Specific Outcomes"
description: |
  - Derive antiviral specific outcomes
  - Exploratory analyses
  - Pre-specified analyses
author: "James Totterdell"
date: today
execute:
  echo: false
  message: false
  warning: false
---

```{r}
#| label: pkgs
#| include: false
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(ASCOTr)

theme_set(theme_classic(base_size = 10, base_family = "Palatino") +
  theme(panel.grid = element_blank(),
        strip.background = element_blank()))
```

```{r}
#| label: load-data
all_data <- readRDS(file.path(ASCOT_DATA, "all_data.rds"))
all_daily_data <- readRDS(file.path(ASCOT_DATA, "all_daily_data.rds"))

saes <- readxl::read_excel(
  file.path(ASCOT_DATA, "explanation", "ASCOT_ADAPT_ListofSAEs.xlsx")) |>
  arrange(`Date of SAE onset`)  

sars <- readxl::read_excel(
  file.path(ASCOT_DATA, "explanation", "ASCOT_ADAPT_ListofSARs.xlsx")) |>
  arrange(`Date of SAE onset`)

bleed <- readxl::read_excel(
  file.path(ASCOT_DATA, "explanation", "Bleeds.xlsx"))
```


## Antiviral Outcomes

A number of domain specific outcomes were of interest for the antiviral interventions:

- viral clearance
- viral load
- Elevation of Alanine Transaminase (ALT) or Aspartate Transaminase (AST)
- Serum Potassium
- Serum Sodium

## Derivations

What follows runs through the derivation of these outcomes from the available data.

### Viral Clearance

*Viral clearance (negative SARS-CoV-2 RT-PCR) at days 3 and 7 will be represented as a binary indicator variable.*

The relevant fields are:

- `DD_RespiratoryPCR_TestDone`: was a PCR test done on this day
- `DD_RespiratorySampleResult`: result of test

There is inconsistent timing of when tests are done (most do not have a test on day 3 or day 7).
Many participants have no tests at all.
Need to consider whether lack of testing related to patient status (too well/ill to bother with/perform testing)?
Will only provide descriptive summaries of available data.

Check how many participants had any tests done:

```{r}
vc_table <- all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |> 
  select(StudyPatientID, DD_StudyDay, AAssignment, DD_RespiratoryPCR_TestDone) |>
  group_by(StudyPatientID, AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1])) |>
  summarise(
    any_tests = any(DD_RespiratoryPCR_TestDone == "Yes"),
    num_tests = sum(DD_RespiratoryPCR_TestDone == "Yes", na.rm = TRUE)) |>
  group_by(AAssignment) |>
  summarise(
    Assigned = sprintf("%i", n()),
    `Any tests` = sprintf("%i", sum(any_tests)),
    Proportion = sprintf("%.2f", mean(any_tests)),
    `Total tests` = sprintf("%i", sum(num_tests)),
    `Mean number of tests` = sprintf("%.2f", mean(num_tests)),
    `Max number of tests` = sprintf("%i", max(num_tests))
  ) |>
  pivot_longer(2:7, names_to = "Variable") |>
  pivot_wider(names_from = AAssignment, values_from = value)

vc_table |> 
  kable("html", digits = 2, align = "lrr") |>
  kable_styling("striped", font_size = 12)

vc_table |> 
  kable("latex", digits = 2, booktabs = TRUE, align = "lrr", linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  save_tex_table("outcomes/domain/patient-viral-clearance")
```

Check how many participants had a test done on each study day:

```{r}
vc_table <- all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |> 
  select(StudyPatientID, DD_StudyDay, AAssignment, DD_RespiratoryPCR_TestDone, DD_RespiratorySampleResult) |>
  group_by(DD_StudyDay, AAssignment) |>
  summarise(
    Patients = sprintf("%i", n()),
    `Tests` = sprintf("%i (%.0f)", 
                          sum(DD_RespiratoryPCR_TestDone == "Yes"), 
                          100 * sum(DD_RespiratoryPCR_TestDone == "Yes") / n()),
    `Positive` = sprintf("%i (%.0f)", 
                       sum(DD_RespiratorySampleResult == "Positive", na.rm = TRUE), 
                       100 * sum(DD_RespiratorySampleResult == "Positive", na.rm = TRUE) / sum(DD_RespiratoryPCR_TestDone == "Yes")),
    `Negative` = sprintf("%i (%.0f)", 
                       sum(DD_RespiratorySampleResult == "Negative", na.rm = TRUE), 
                       100 * sum(DD_RespiratorySampleResult == "Negative", na.rm = TRUE) / sum(DD_RespiratoryPCR_TestDone == "Yes")),
    `Indeterminate` = sprintf("%i (%.0f)", 
                       sum(DD_RespiratorySampleResult == "Indeterminate", na.rm = TRUE), 
                       100 * sum(DD_RespiratorySampleResult == "Indeterminate", na.rm = TRUE) / sum(DD_RespiratoryPCR_TestDone == "Yes")),
  )  |>
  ungroup() |>
  pivot_wider(names_from = AAssignment, values_from = Patients:Indeterminate) |>
  select(DD_StudyDay, ends_with("A1"), ends_with("A2")) |>
  filter(DD_StudyDay < 8)
colnames(vc_table) <- gsub("_A[1-2]", "", colnames(vc_table))
colnames(vc_table)[1] <- "Day"

vc_table |>  
  kable(
    "latex", 
    digits = 2,
    align = "r",
    linesep = "",
    booktabs = TRUE) |>
  kable_styling(latex_options = "HOLD_position", font_size = 8) |>
  add_header_above(c(" " = 1, "Standard of care" = 5, "Nafamostat" = 5)) |>
  save_tex_table(fn = "outcomes/domain/daily-viral-clearance")

vc_table |>  
  kable(
    "html", 
    digits = 2,
    align = "r"
  ) |>
  kable_styling("striped", font_size = 11) |>
  add_header_above(c(" " = 1, "Standard of care" = 5, "Nafamostat" = 5))
```

Check sequence of test results across participants (note `NA` means no test done):

```{r}
all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0", DD_StudyDay %in% 1:8) |> 
  select(StudyPatientID, DD_StudyDay, DD_RespiratorySampleResult) |> 
  pivot_wider(names_from = DD_StudyDay, values_from = DD_RespiratorySampleResult) |> 
  kable("html", digits = 2) |>
  kable_styling("striped", font_size = 11)
```

### Viral Load

*Viral load is based on the cycle threshold (Ct) value in reverse transcription polymerase chain reaction (RT-PCR).*
*Viral load at day 3 and day 7 will be reported as the median number (and IQR) of process cycles it takes for the fluorescent signal to exceed the background level.*
*Change in viral load from baseline to day 3 and to day 7 will be summarised similarly.*

Note that the cycle threshold refers to the number of process cycles it takes for the fluorescent signal to exceed the background level.
Low cycle numbers imply high levels of viral load. Multiple assays were used and therefore any interpretation will be limited.

The relevant fields are:

- `BAS_CycleThresholdValue`: baseline cycle threshold value
- `DD_RespiratorySampleResult`: result of test
- `DD_CycleThreshold`: cycle threshold value (only if `DD_RespiratorySampleResult = "Positive"`)
- `DD_PCRMethod`: type of test

Very few participants (24 of 156) had baseline cycle threshold recorded so there will be very little data for looking at change in viral load from baseline.

```{r}
all_data |>
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  count(BAS_CycleThresholdKnown)
```

```{r}
vl_table <- all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |> 
  select(StudyPatientID, DD_StudyDay, AAssignment, DD_CycleThreshold) |>
  group_by(StudyPatientID, AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1])) |>
  summarise(
    any_tests = any(!is.na(DD_CycleThreshold)),
    num_tests = sum(!is.na(DD_CycleThreshold))
  ) |>
  group_by(AAssignment) |>
  summarise(
    Assigned = sprintf("%i", n()),
    `Any Ct values` = sprintf("%i (%.0f)", sum(any_tests), 100 * sum(any_tests) / n()),
    `Total Ct values` = sprintf("%i", sum(num_tests)),
    `Max number of Ct values` = sprintf("%i", max(num_tests))
  ) |>
  pivot_longer(2:5, names_to = "Variable") |>
  pivot_wider(names_from = AAssignment, values_from = value)

vl_table |> 
  kable("html", digits = 2, align = "lrr") |>
  kable_styling("striped", font_size = 12)

vl_table |> 
  kable("latex", digits = 2, booktabs = TRUE, align = "lrr", linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  save_tex_table("outcomes/domain/patient-viral-load")
```

```{r}
tt <- all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0", DD_StudyDay %in% 1:8) |> 
  select(StudyPatientID, AAssignment, DD_StudyDay, DD_RespiratoryPCR_TestDone, DD_RespiratorySampleResult, DD_CycleThreshold) |> 
  group_by(DD_StudyDay, AAssignment) |>
  summarise(
    Patients = sprintf("%i", n()),
    `Tests` = sprintf("%i (%.0f)", 
                          sum(DD_RespiratoryPCR_TestDone == "Yes"), 
                          100 * sum(DD_RespiratoryPCR_TestDone == "Yes") / n()),
    `Positive` = sprintf("%i (%.0f)", 
                       sum(DD_RespiratorySampleResult == "Positive", na.rm = TRUE), 
                       100 * sum(DD_RespiratorySampleResult == "Positive", na.rm = TRUE) / sum(DD_RespiratoryPCR_TestDone == "Yes")),
    `Ct value` = sprintf("%i (%.0f)", 
                       sum(!is.na(DD_CycleThreshold)), 
                       100 * sum(!is.na(DD_CycleThreshold)) / sum(DD_RespiratorySampleResult == "Positive", na.rm = TRUE)),
    `Median Ct value` = sprintf("%.0f", median(as.numeric(DD_CycleThreshold), na.rm = TRUE))
  ) |>
  ungroup() |>
  pivot_wider(names_from = AAssignment, values_from = Patients:`Median Ct value`) |>
  select(DD_StudyDay, ends_with("A1"), ends_with("A2"))

colnames(tt) <- gsub("_A[1-2]", "", colnames(tt))
colnames(tt)[1] <- "Day"

tt |>  
  kable(
    "latex", 
    digits = 2,
    align = "lrrrrrrrrrr",
    linesep = "",
    booktabs = TRUE) |>
  kable_styling(latex_options = "HOLD_position", font_size = 8) |>
  add_header_above(c(" " = 1, "Standard of care" = 5, "Nafamostat" = 5)) |>
  save_tex_table(fn = "outcomes/domain/daily-viral-load")

tt |>
  kable("html", digits = 2, align = "lrrrrrrrrrr") |>
  kable_styling("striped", font_size = 11) |>
  add_header_above(c(" " = 1, "Standard of care" = 5, "Nafamostat" = 5))
```

```{r}
p <- all_daily_data |>
  filter_avs_itt() |>
  filter(!is.na(DD_CycleThreshold), DD_StudyDay < 8) |>
  select(StudyPatientID, AAssignment, DD_StudyDay, DD_CycleThreshold) |>
  mutate(DD_CycleThreshold = as.numeric(DD_CycleThreshold),
         AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1])) |>
  ggplot(aes(DD_StudyDay, DD_CycleThreshold)) +
  facet_wrap( ~ AAssignment) +
  geom_point() +
  geom_line(aes(group = StudyPatientID)) +
  labs(x = "Study day", y = "Cycle threshold value")
ggsave(
  file.path("outputs", "figures", "outcomes", "domain", "ct-values.pdf"),
  p,
  height = 2,
  width = 4,
  dpi = 244
)
```

### Elevation of Alanine Transaminase (ALT) or Aspartate Transaminase (AST)

Elevation of Alanine Transaminase (ALT) or Aspartate Transaminase (AST) to more than 5 times the upper limit of normal will be represented as a binary indicator variable.

The relevant fields are:

- `DD_ALTLabs`: ALT
- `DD_ASTLabs`: AST

These are lab values reported in IU/L.
However there is no indication as to what the "upper limit of normal" is.
In the dictionary it states "If ALT > 150 IU/L show alert: Clinician to evaluate whether this is an SAR and consider discontinuation of nafamostat."
Not sure if this 150 value relates to the "5 times upper limit of normal".
Will need advice from the antiviral group.

```{r}
#| label: tbl-daily-alt-ast-individual
#| tbl-cap: Summary of individual daily ALT and AST tests (IU/L).
tt <- all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  select(StudyPatientID, DD_StudyDay, AAssignment, DD_ALTLabs, DD_ASTLabs) |>
  group_by(StudyPatientID, AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1])) |>
  summarise(
    days = n(),
    any_alt_tests = any(!is.na(DD_ALTLabs)),
    any_ast_tests = any(!is.na(DD_ASTLabs)),
    any_alt_gt150 = any(DD_ALTLabs > 150, na.rm = TRUE),
    any_ast_gt150 = any(DD_ASTLabs > 150, na.rm = TRUE),
    n_alt_tests = sum(!is.na(DD_ALTLabs)),
    n_ast_tests = sum(!is.na(DD_ASTLabs)),
    n_alt_gt150 = sum(DD_ALTLabs > 150, na.rm = TRUE),
    n_ast_gt150 = sum(DD_ASTLabs > 150, na.rm = TRUE)
  )

tt_tab <- tt |> 
  group_by(AAssignment) |>
  summarise(
    Assigned = sprintf("%i", n()),
    `Any ALT tests, n (% of assigned)` = sprintf("%i (%.0f)", sum(any_alt_tests), 100 * sum(any_alt_tests) / n()),
    `Any ALT > 150, n (% of tested)` = sprintf("%i (%.0f)", sum(any_alt_gt150), 100 * sum(any_alt_gt150) / sum(any_alt_tests)),
    `Any AST tests, n (% of assigned)` = sprintf("%i (%.0f)", sum(any_ast_tests), 100 * sum(any_ast_tests) / n()),
    `Any AST > 150, n (% of tested)` = sprintf("%i (%.0f)", sum(any_ast_gt150), 100 * sum(any_ast_gt150) / sum(any_ast_tests)),
    `Total days` = sprintf("%i", sum(days)),
    `Total days ALT tested, n (% of days)` = sprintf("%i (%.0f)", sum(n_alt_tests), 100 * sum(n_alt_tests) / sum(days)),
    `Total days ALT > 150, n (% of tests)` = sprintf("%i (%.0f)", sum(n_alt_gt150), 100 * sum(n_alt_gt150) / sum(n_alt_tests)),
    `Total days AST tested, n (% of days)` = sprintf("%i (%.0f)", sum(n_ast_tests), 100 * sum(n_ast_tests) / sum(days)),
    `Total days AST > 150, n (% of tests)` = sprintf("%i (%.0f)", sum(n_ast_gt150), 100 * sum(n_ast_gt150) / sum(n_ast_tests))
  ) |>
  pivot_longer(2:11, names_to = "Variable") |>
  pivot_wider(names_from = AAssignment, values_from = value)

tt_tab |>
  kable("html", digits = 2, align = "lrr") |>
  kable_styling("striped", font_size = 12)

tt_tab |>
  kable("latex", booktabs = TRUE, digits = 2, align = "lrr") |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  save_tex_table("outcomes/domain/patient-alt-ast")
```

Check daily tests:

```{r}
#| label: tbl-daily-alt
#| tbl-cap: Summary of daily ALT levels.
alt_table <- all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  select(StudyPatientID, DD_StudyDay, AAssignment, DD_ALTLabs, DD_ASTLabs) |>
  group_by(AAssignment, DD_StudyDay) |>
  summarise(
    n = n(),
    alt_tests = sprintf("%i (%0.f)", sum(!is.na(DD_ALTLabs)), 100 *  sum(!is.na(DD_ALTLabs)) / n),
    alt_median = sprintf("%.0f", median(DD_ALTLabs, na.rm = TRUE)),
    alt_gt150_tests = sprintf(
      "%i (%0.f)", 
      sum(DD_ALTLabs > 150, na.rm = TRUE), 
      100 * sum(DD_ALTLabs > 150, na.rm = TRUE) / sum(!is.na(DD_ALTLabs)))
  ) |>
  ungroup() |>
  pivot_wider(names_from = AAssignment, values_from = n:alt_gt150_tests) |>
  select(DD_StudyDay, ends_with("A1"), ends_with("A2"))
clab <- c("Study Day", rep(c("Patients", "Tested\n(\\% of patients)", "Median", "> 150 IU/L\n(\\% of tests)"), times = 2))

alt_table |>  
  kable(
    "latex", 
    digits = 2,
    align = "r",
    booktabs = TRUE,
    col.names = linebreak(clab, align = "c"),
    escape = FALSE) |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  add_header_above(c(" " = 1, "Standard of care" = 4, "Nafamostat" = 4)) |>
  save_tex_table(fn = "outcomes/domain/daily-alt")

alt_table |>  
  kable(
    "html", 
    digits = 2,
    align = "r",
    col.names = clab) |>
  kable_styling("striped", font_size = 11) |>
  add_header_above(c(" " = 1, "Standard of care" = 4, "Nafamostat" = 4))
```

```{r}
#| label: tbl-daily-ast
#| tbl-cap: Summary of daily AST levels.
ast_table <- all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  select(StudyPatientID, DD_StudyDay, AAssignment, DD_ASTLabs) |>
  group_by(AAssignment, DD_StudyDay) |>
  summarise(
    n = n(),
    ast_tests = sprintf("%i (%0.f)", sum(!is.na(DD_ASTLabs)), 100 *  sum(!is.na(DD_ASTLabs)) / n),
    ast_median = sprintf("%.0f", median(DD_ASTLabs, na.rm = TRUE)),
    ast_gt150_tests = sprintf(
      "%i (%0.f)", 
      sum(DD_ASTLabs > 150, na.rm = TRUE), 
      100 * sum(DD_ASTLabs > 150, na.rm = TRUE) / sum(!is.na(DD_ASTLabs)))
  ) |>
  ungroup() |>
  pivot_wider(names_from = AAssignment, values_from = n:ast_gt150_tests) |>
  select(DD_StudyDay, ends_with("A1"), ends_with("A2"))
clab <- c("Study Day", rep(c("Patients", "Tested\n(\\% of patients)", "Median", "> 150 IU/L\n(\\% of tests)"), times = 2))

ast_table |>  
  kable(
    "latex", 
    digits = 2,
    align = "r",
    booktabs = TRUE,
    col.names = linebreak(clab, align = "c"),
    escape = FALSE) |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  add_header_above(c(" " = 1, "Standard of care" = 4, "Nafamostat" = 4)) |>
  save_tex_table(fn = "outcomes/domain/daily-ast")

ast_table |>  
  kable(
    "html", 
    digits = 2,
    align = "r",
    col.names = clab) |>
  kable_styling("striped", font_size = 11) |>
  add_header_above(c(" " = 1, "Standard of care" = 4, "Nafamostat" = 4))
```

```{r}
tt <- all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  select(StudyPatientID, DD_StudyDay, AAssignment, DD_ALTLabs, DD_ASTLabs) |>
  group_by(StudyPatientID, AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1])) |>
  summarise(
    days = n(),
    any_altorast_tests = any(!is.na(DD_ALTLabs) | !is.na(DD_ALTLabs)),
    any_altorast_gt150 = any(DD_ALTLabs > 150 | DD_ASTLabs > 150, na.rm = TRUE),
    n_altorast_tests = sum(!is.na(DD_ALTLabs) | !is.na(DD_ASTLabs)),
    n_altorast_gt150 = sum(DD_ALTLabs > 150 | DD_ASTLabs > 150, na.rm = TRUE)
  )

tt_tab <- tt |> 
  group_by(AAssignment) |>
  summarise(
    Assigned = sprintf("%i", n()),
    `Any ALT or AST tests, n (% of assigned)` = sprintf("%i (%.0f)", sum(any_altorast_tests), 100 * sum(any_altorast_tests) / n()),
    `Any ALT > 150 or AST > 150, n (% of tested)` = sprintf("%i (%.0f)", sum(any_altorast_gt150), 100 * sum(any_altorast_gt150) / sum(any_altorast_tests)),
    `Total days` = sprintf("%i", sum(days)),
    `Total days ALT or AST tested, n (% of days)` = sprintf("%i (%.0f)", sum(n_altorast_tests), 100 * sum(n_altorast_tests) / sum(days)),
    `Total days ALT > 150 or AST > 150, n (% of tests)` = sprintf("%i (%.0f)", sum(n_altorast_gt150), 100 * sum(n_altorast_gt150) / sum(n_altorast_tests))
    )|>
  pivot_longer(2:7, names_to = "Variable") |>
  pivot_wider(names_from = AAssignment, values_from = value)

tt_tab |>
  kable("html", digits = 2, align = "lrr") |>
  kable_styling("striped", font_size = 12)

tt_tab |>
  kable("latex", booktabs = TRUE, digits = 2, align = "lrr") |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  save_tex_table("outcomes/domain/patient-alt-or-ast")
```


### Elevation of serum potassium

Elevation of serum potassium to more than 5.5 mmol/L will be represented as a binary indicator variable.

- `DD_Potassium`

Some potential challenges with this outcome: 

- not all participants are tested as often as each other, some have no tests. Missing test may be NAR: worse appearing patients may be more/less likely to have had a test and may have higher/lower potassium levels
- participants who stay in hospital longer may be more severe and so have higher potassium levels, so any summary looking at averages or counts over variable follow-up time may have issues if this is not accounted for.

Check baseline potassium (should be zero who exceed 5.5 as it was eligibility requirement):

```{r}
#| label: tbl-baseline-potassium
#| tbl-cap: Baseline serum potassium (mmol/L).
all_data |>
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  select(StudyPatientID, AAssignment, EL_SerumPotassium) |>
  group_by(AAssignment) |>
  summarise(
    n = n(),
    mean = mean(EL_SerumPotassium),
    n_gt55 = sum(EL_SerumPotassium > 5.5)
  ) |>
  kable("html", digits = 2) |>
  kable_styling("striped", font_size = 12)
```

Check participant summaries:

```{r}
#| label: tbl-daily-potassium-individual
#| tbl-cap: Summary of individual daily serum potassium (mmol/L) levels.
tt <- all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  select(StudyPatientID, DD_StudyDay, AAssignment, DD_Potassium) |>
  group_by(StudyPatientID, AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1])) |>
  summarise(
    days = n(),
    any_tests = any(!is.na(DD_Potassium)),
    tests = sum(!is.na(DD_Potassium)),
    any_gt55 = as.numeric(any(DD_Potassium > 5.5, na.rm = TRUE)),
    n_gt55 = sum(DD_Potassium > 5.5, na.rm = TRUE),
    max_val = max(DD_Potassium, na.rm = TRUE),
    all_val_gt55 = paste0(DD_Potassium[which(DD_Potassium > 5.5)], collapse = ", ")
  )
sp_table <- tt |> 
  group_by(AAssignment) |>
  summarise(
    Assigned = n(),
    `Any tests` = sum(any_tests),
    `Any > 5.5 mmol/L` = sum(any_gt55),
    `Total days` = sum(days),
    `Total tests` = sum(tests),
    `Total > 5.5 mmol/L` = sum(n_gt55)
  ) |>
  pivot_longer(2:7, names_to = "Variable") |>
  pivot_wider(names_from = AAssignment, values_from = value)
  kable("html", digits = 2) |>
  kable_styling("striped", font_size = 12)
  
sp_table |> 
  kable("html", digits = 2, align = "lrr") |>
  kable_styling("striped", font_size = 12)

sp_table |> 
  kable("latex", digits = 2, booktabs = TRUE, align = "lrr", linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  save_tex_table("outcomes/domain/patient-serum-potassium")
```

Check daily potassium tests:

```{r}
#| label: tbl-daily-potassium
#| tbl-cap: Summary of daily potassium levels.
sp_table <- all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  select(StudyPatientID, DD_StudyDay, AAssignment, DD_Potassium) |>
  group_by(AAssignment, DD_StudyDay) |>
  summarise(
    n = n(),
    tests = sprintf("%i (%0.f)", sum(!is.na(DD_Potassium)), 100 *  sum(!is.na(DD_Potassium)) / n),
    mean = mean(DD_Potassium, na.rm = TRUE),
    gt55 = sprintf("%i (%.0f)", 
                   sum(DD_Potassium > 5.5, na.rm = TRUE), 
                   100 * sum(DD_Potassium > 5.5, na.rm = TRUE) / sum(!is.na(DD_Potassium))),
  ) |>
  ungroup() |>
  pivot_wider(names_from = AAssignment, values_from = n:gt55) |>
  select(DD_StudyDay, ends_with("A1"), ends_with("A2"))

clab <- c("Study Day", rep(c("Patients", "Tested\n(\\% of patients)", "Mean", "> 5.5\n(\\% of tests)"), times = 2))

sp_table |>  
  kable(
    "latex", 
    digits = 2,
    align = "r",
    booktabs = TRUE,
    col.names = linebreak(clab, align = "c"),
    escape = FALSE) |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  add_header_above(c(" " = 1, "Standard of care" = 4, "Nafamostat" = 4)) |>
  save_tex_table(fn = "outcomes/domain/daily-serum-potassium")

sp_table |>  
  kable(
    "html", 
    digits = 2,
    align = "r",
    col.names = c("Study Day", rep(c("Patients", "Tested (%)", "Mean", "> 5.5 (%)"), times = 2))) |>
  kable_styling("striped", font_size = 11) |>
  add_header_above(c(" " = 1, "Standard of care" = 4, "Nafamostat" = 4))
```

Check SARS/SAES

```{r}
events <- bind_rows(
  saes |> select(`Patient ID`, `Date of SAE onset`, `SAE Term`, `Notes from Site`) |> mutate(Type = "SAE"),
  sars |> select(`Patient ID`, `Date of SAE onset`, `SAE Term`, `Notes from Site`) |> mutate(Type = "SAR")
) |>
  rename(`Onset date` = `Date of SAE onset`) |>
  mutate(`Onset date` = as.Date(`Onset date`)) |>
  select(`Patient ID`, `Onset date`, `SAE Term`, Type, `Notes from Site`)
tt |> 
  filter(any_gt55 == 1) |>
  select(StudyPatientID, Antiviral = AAssignment, Values = all_val_gt55) |>
  left_join(
    events |> filter(grepl("hyper", tolower(`SAE Term`))), by = c("StudyPatientID" = "Patient ID")
  ) |>
  mutate(
    across(where(is.character), ~replace_na(.x, ""))
  ) |>
  rename(ID = StudyPatientID) |>
  kable(
    "latex",
    booktabs = TRUE,
    align = "l",
    linesep = ""
  ) |>
  kable_styling(
    latex_options = "HOLD_position",
    font_size = 5.5
  ) |>
  column_spec(1:5, width = "1cm") |>
  column_spec(6, width = "0.5cm") |>
  column_spec(7, width = "6cm") |>
  save_tex_table("outcomes/domain/sae-serum-potassium")
```

### Decrease of serum sodium

Decrease of serum sodium to less than 125 mmol/L will be represented as a binary indicator variable.

- `DD_Sodium`

Only one participant had elevated serum sodium.
This was on two consecutive days (study day 26 and 27).

Check baseline sodium (should be zero who less than 125 as it was eligibility requirement):

```{r}
#| label: tbl-baseline-sodium
#| tbl-cap: Baseline serum sodium (mmol/L).
all_data |>
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  select(StudyPatientID, AAssignment, EL_SerumSodium) |>
  group_by(AAssignment) |>
  summarise(
    n = n(),
    mean = mean(EL_SerumSodium),
    n_lt125 = sum(EL_SerumSodium < 125)
  ) |>
  kable("html", digits = 2) |>
  kable_styling("striped", font_size = 12)
```

Check participant summaries:

```{r}
#| label: tbl-daily-sodium-individual
#| tbl-cap: Summary of individual daily serum sodium (mmol/L) levels.
tt <- all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  select(StudyPatientID, DD_StudyDay, AAssignment, DD_Sodium) |>
  group_by(StudyPatientID, AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1])) |>
  summarise(
    days = n(),
    any_tests = any(!is.na(DD_Sodium)),
    tests = sum(!is.na(DD_Sodium)),
    any_lt125 = as.numeric(any(DD_Sodium < 125, na.rm = TRUE)),
    n_lt125 = sum(DD_Sodium < 125, na.rm = TRUE)
  )
ss_table <- tt |> 
  group_by(AAssignment) |>
  summarise(
    Assigned = n(),
    `Any tests` = sum(any_tests),
    `Any < 125 mmol/L` = sum(any_lt125),
    `Total days` = sum(days),
    `Total tests` = sum(tests),
    `Total < 125 mmol/L` = sum(n_lt125)
  ) |>
  pivot_longer(2:7, names_to = "Variable") |>
  pivot_wider(names_from = AAssignment, values_from = value)

ss_table |> 
  kable("html", digits = 2, align = "lrr") |>
  kable_styling("striped", font_size = 12)

ss_table |> 
  kable("latex", digits = 2, booktabs = TRUE, align = "lrr", linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  save_tex_table("outcomes/domain/patient-serum-sodium")
```

Check daily sodium tests:

```{r}
#| label: tbl-daily-sodium
#| tbl-cap: Summary of daily sodium levels (mmol/L).
ss_table <- all_daily_data |> 
  filter(ENR_rec == 1, WTH_FU == 0, AAssignment != "A0") |>
  select(StudyPatientID, DD_StudyDay, AAssignment, DD_Sodium) |>
  group_by(AAssignment, DD_StudyDay) |>
  summarise(
    n = n(),
    tests = sprintf("%i (%.0f)", sum(!is.na(DD_Sodium)), 100 * sum(!is.na(DD_Sodium)) / n),
    mean = mean(DD_Sodium, na.rm = TRUE),
    lt125 = sprintf("%i (%.0f)", 
                    sum(DD_Sodium < 125, na.rm = TRUE), 
                    100 * sum(DD_Sodium < 125, na.rm = TRUE) / sum(!is.na(DD_Sodium))),
  ) |>
  ungroup() |>
  pivot_wider(names_from = AAssignment, values_from = n:lt125) |>
  select(DD_StudyDay, ends_with("A1"), ends_with("A2"))

clab <- c("Study Day", rep(c("Patients", "Tested\n(\\% of patients)", "Mean", "< 125\n(\\% of tests)"), times = 2))

ss_table |>  
  kable(
    "latex", 
    digits = 2,
    align = "r",
    booktabs = TRUE, escape = FALSE,
    col.names = linebreak(clab, linebreaker = "\n", align = "c")) |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  add_header_above(c(" " = 1, "Standard of care" = 4, "Nafamostat" = 4)) |>
  save_tex_table(fn = "outcomes/domain/daily-serum-sodium")

ss_table |>  
  kable(
    "html", 
    digits = 2,
    align = "r",
    col.names = clab) |>
  kable_styling("striped", font_size = 11) |>
  add_header_above(c(" " = 1, "Standard of care" = 4, "Nafamostat" = 4))
```

### Major Bleeding per ISTH

The relevant fields are:

- `DD_AE_C_MajorBleedingISTH`
- `D28_AECMajorBleeding`

```{r}
all_data |>
  filter_avs_itt() |>
  group_by(AAssignment) |>
  summarise(
    Patients = n(),
    `Day 28 major bleeding` = sum(D28_AECMajorBleeding == "Yes")
  )

dd <- all_daily_data |>
  filter_avs_itt() |>
  group_by(
    StudyPatientID, 
    AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1])
  ) |>
  summarise(
    days = n(),
    any_major_bleeding = any(DD_AE_C_MajorBleedingISTH == "Yes"),
    major_bleeding = sum(DD_AE_C_MajorBleedingISTH == "Yes")
  )
mb_table <- dd |>
  group_by(AAssignment) |>
  summarise(
    Assigned = n(),
    `Total days in hospital` = sum(days),
    `Any major bleeding (patient)` = sum(any_major_bleeding),
    `Total major bleeding (days)` = sum(major_bleeding)
  ) |>
  pivot_longer(names_to = "Variable", 2:5) |>
  pivot_wider(names_from = AAssignment, values_from = value)

mb_table |> 
  kable("html", digits = 2, align = "lrr") |>
  kable_styling("striped", font_size = 12)

mb_table |> 
  kable("latex", digits = 2, booktabs = TRUE, align = "lrr", linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  save_tex_table("outcomes/domain/patient-major-bleeding")
```

A SAR was recorded in correspondence with this major bleeding event.

```{r}
sars |> 
  filter(`Patient ID` == "WES00039") |>
  mutate(`Onset Date` = as.Date(`Date of SAE onset`)) |>
  select(`Patient ID`, `Date of SAE onset`, `Concurrant Disorder / Medication?`, `Notes from Site`) |>
  kable(
    "latex",
    booktabs = TRUE, 
    align = "l"
  ) |>
  kable_styling(latex_options = "HOLD_position", font_size = 5.5) |>
  column_spec(1:2, width = "1cm") |>
  column_spec(3, width = "2cm") |>
  column_spec(4, width = "9cm") |>
  save_tex_table("outcomes/safety/sars-major-bleed")
```

### Clinically Relevant non-major bleeding

The relevant fields are:

- `D28_ABNonMajorBleeding` (appears missing if not randomised to anticoagulation)
- `DIS_NonMajorBleeding` (appears missing for many participants)

```{r}
all_data |>
  filter_avs_itt() |>
  count(AAssignment, CAssignment, DIS_NonMajorBleeding) |>
  spread(CAssignment, n)

all_data |>
  filter_avs_itt() |>
  count(AAssignment, CAssignment, D28_ABNonMajorBleeding) |>
  spread(CAssignment, n)

all_data |>
  count(AAssignment, D28_ABNonMajorBleeding, DIS_NonMajorBleeding) |>
  spread(DIS_NonMajorBleeding, n)

all_data |>
  count(CAssignment, D28_ABNonMajorBleeding, DIS_NonMajorBleeding) |>
  spread(DIS_NonMajorBleeding, n)

all_data |>
  filter(AAssignment != "A0", CAssignment != "C0") |>
  count(D28_ABNonMajorBleeding, DIS_NonMajorBleeding) |>
  spread(D28_ABNonMajorBleeding, n, fill = 0) |>
  kable() |>
  kable_styling() |>
  add_header_above(c(" " = 1, "D28_ABNonMajorBleeding" = 4))
```

```{r}
nmb_dat <- all_data |>
  filter_avs_itt() |>
  mutate(
    mb = case_when(
      D28_ABNonMajorBleeding == "Yes" ~ 1,
      DIS_NonMajorBleeding == "Yes" ~ 1,
      DIS_NonMajorBleeding == "No" ~ 0, 
      D28_ABNonMajorBleeding == "No" ~ 0,
      TRUE ~ NA_real_
    )
  ) |>
  group_by(AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1])) |>
  summarise(
    Assigned = n(),
    Missing = sum(is.na(mb)),
    `Any non-major bleeding` = sum(mb, na.rm = TRUE)
  ) |>
  pivot_longer(names_to = "Variable", 2:4) |>
  pivot_wider(names_from = AAssignment, values_from = value)

nmb_dat |> 
  kable("html", digits = 2, align = "lrr") |>
  kable_styling("striped", font_size = 12)

nmb_dat |> 
  kable("latex", digits = 2, booktabs = TRUE, align = "lrr", linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  save_tex_table("outcomes/domain/patient-non-major-bleeding")
```

```{r}
all_data |>
  filter_avs_itt() |>
  select(StudyPatientID, AAssignment, CAssignment, D28_ABNonMajorBleeding, DIS_NonMajorBleeding) |>
  filter(D28_ABNonMajorBleeding == "Yes" | DIS_NonMajorBleeding == "Yes") |>
  left_join(
    sars |> select(`Patient ID`, `Notes from Site`), by = c("StudyPatientID" = "Patient ID")
  )
```

A SAR was recorded in correspondence with the two non-major bleeding events reported on the day 28 form.

```{r}
sars |> 
  filter(`Patient ID` %in% c("MID00009", "RPH00005")) |>
  mutate(`Onset Date` = as.Date(`Date of SAE onset`)) |>
  select(`Patient ID`, `Date of SAE onset`, `Concurrant Disorder / Medication?`, `Notes from Site`) |>
  kable(
    "latex",
    booktabs = TRUE, 
    align = "l"
  ) |>
  kable_styling(latex_options = "HOLD_position", font_size = 5.5) |>
  column_spec(1:2, width = "1cm") |>
  column_spec(3, width = "2cm") |>
  column_spec(4, width = "9cm") |>
  save_tex_table("outcomes/safety/sars-non-major-bleed")
```

For the other non-major bleeds, follow-up with sites was conducted and summaries provided.

```{r}
all_data |>
  filter_avs_itt() |>
  filter(D28_ABNonMajorBleeding == "Yes" | DIS_NonMajorBleeding == "Yes") |>
  select(StudyPatientID, AAssignment, CAssignment) |>
  mutate(
    Antiviral = factor(AAssignment, 
                       levels = c("A0", "A1", "A2"), 
                       labels = intervention_labels2()$AAssignment),
    Anticoagulation = factor(CAssignment,
                             levels = c("C0", "C1", "C2", "C3", "C4"),
                             labels = intervention_labels2()$CAssignment)) |>
  select(-AAssignment, -CAssignment) |>
  left_join(
    bleed |> select(`Patient ID`, `Notes from Site`), by = c("StudyPatientID" = "Patient ID")
  ) |>
  filter(!is.na(`Notes from Site`)) |>
  kable(
    "latex",
    booktabs = TRUE, 
    align = "l"
  ) |>
  kable_styling(latex_options = "HOLD_position", font_size = 5.5) |>
  column_spec(1:2, width = "1cm") |>
  column_spec(3, width = "2cm") |>
  column_spec(4, width = "9cm") |>
  save_tex_table("outcomes/safety/non-major-bleed-other")
```


```{r}
nmb_dat <- all_data |>
  filter_fas_itt() |>
  group_by(
    Antiviral = factor(AAssignment, labels = intervention_labels2()$AAssignment),
    Anticoagulation = factor(CAssignment, labels = intervention_labels2()$CAssignment)) |>
  summarise(
    Assigned = n(),
    Missing = sum(is.na(D28_ABNonMajorBleeding)),
    `Day 28 non-major bleeding` = sum(D28_ABNonMajorBleeding == "Yes", na.rm = TRUE)
  )
```

### All Bleeding

```{r}
dd <- all_daily_data |>
  filter_avs_itt() |>
  group_by(
    StudyPatientID, 
    AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1]),
    CAssignment = factor(CAssignment, labels = intervention_labels2()$CAssignment)
  ) |>
  summarise(
    days = n(),
    dd_mb = as.integer(any(DD_AE_C_MajorBleedingISTH == "Yes")),
    dd_mb_days = sum(DD_AE_C_MajorBleedingISTH == "Yes")
  ) |>
  ungroup()
d <- all_data |>
  filter_avs_itt() |>
  transmute(
    StudyPatientID,
    d28_mb = as.integer(D28_AECMajorBleeding == "Yes"),
    d28_nmb = case_when(
      DIS_NonMajorBleeding == "Yes" ~ 1,
      D28_ABNonMajorBleeding == "Yes" ~ 1,
      DIS_NonMajorBleeding == "No" ~ 0,
      D28_ABNonMajorBleeding == "No" ~ 0,
      TRUE ~ NA_real_
    )
  )
ddd <- dd |> left_join(d, by = "StudyPatientID")

ddd |>
  group_by(AAssignment) |>
  summarise(
    Assigned = sprintf("%i", n()),
    `Major bleeding` = sprintf("%i", sum(dd_mb | d28_mb)),
    `Non-major bleeding` = sprintf("%i", sum(d28_nmb, na.rm = TRUE)),
    `Any bleeding` = sprintf("%i", sum(dd_mb | d28_mb | d28_nmb, na.rm = TRUE))
  ) |>
  pivot_longer(2:5, names_to = "Variable") |>
  pivot_wider(names_from = "AAssignment", values_from = value) |> 
  kable("latex", digits = 2, booktabs = TRUE, align = "lrr", linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  save_tex_table("outcomes/domain/patient-bleeding")

ddd |>
  filter(dd_mb == 1 | d28_mb == 1 | d28_nmb == 1) |>
  transmute(
    ID = StudyPatientID,
    Antiviral = AAssignment,
    Anticoagulation = CAssignment,
    Bleeding = case_when(
      dd_mb == 1 ~ "Major",
      d28_mb == 1 ~ "Major",
      d28_nmb == 1 ~ "Non-major",
      TRUE ~ NA_character_
    )
  ) |> 
  kable("latex", digits = 2, booktabs = TRUE, align = "l", linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  save_tex_table("outcomes/domain/patient-bleeding-listing")
```

### Thrombo

Relevant fields are:

- `DIS_ThrombophlebitisIVLine`

```{r}
thromb_table <- all_data |>
  filter_avs_itt() |>
  group_by(AAssignment = factor(AAssignment, labels = intervention_labels2()$AAssignment[-1])) |>
  summarise(
    Assigned = sprintf("%i", n()),
    `Thrombophlebitis/vasculitis at IV line site (%)` = 
      sprintf("%i (%.0f)", 
              sum(DIS_ThrombophlebitisIVLine == "Yes"),
              100 * sum(DIS_ThrombophlebitisIVLine == "Yes") / n()
      )
  ) |>
  pivot_longer(names_to = "Variable", 2:3) |>
  pivot_wider(names_from = AAssignment, values_from = value)

thromb_table |> 
  kable("html", digits = 2, align = "lrr") |>
  kable_styling("striped", font_size = 12)

thromb_table |> 
  kable("latex", digits = 2, booktabs = TRUE, align = "lrr", linesep = "") |>
  kable_styling(latex_options = "HOLD_position", font_size = 9) |>
  save_tex_table("outcomes/domain/patient-thrombo")
```

### Anticoagulation

The SAP specifies that some of the outcomes should be stratiied by the anticoagulation treatment received.
Relevant fields are:

- `CAssignment`
- `DIS_AntiCoagTreatment`

```{r}
all_data |>
  filter_avs_itt() |>
  count(CAssignment, DIS_AntiCoagTreatment)
```
