---
title: "Baseline C-Reactive Protein Units"
author: "James Totterdell"
date: today
date-format: long
format:
  pdf:
    documentclass: scrartcl
    linestretch: "1.2"
    mainfont: TeX Gyre Pagella
    mathfont: TeX Gyre Pagella Math
    monofont: TeX Gyre Cursor
    sansfont: TeX Gyre Heros
execute: 
  echo: false
  message: false
  warning: false
---

```{r}
#| label: pkgs
#| include: false
library(tidyverse)
library(kableExtra)
library(labelled)
library(lubridate)
library(patchwork)
library(ASCOTr)

theme_set(theme_classic(base_size = 10, base_family = "Palatino") +
  theme(panel.grid = element_blank(),
        strip.background = element_blank()))
```

```{r}
#| label: load-data
all_data <- readRDS(file.path(ASCOT_DATA, "all_data.rds"))
all_daily_data <- readRDS(file.path(ASCOT_DATA, "all_daily_data.rds"))
```

## Data

In the trial database there are three variables which relate to baseline CRP:

- `BAS_CRPEntered`: Highest CRP last 24 hours entered
- `BAS_CRPUnits`: Highest CRP last 24 hours units
- `BAS_CRPResult`: Highest CRP last 24 hours mg/L

The variable `BAS_CRPEntered` is what was entered in the reported units `BAS_CRPUnits` and `BAS_CRPResult` applies a conversion where necessary so all CRP's are in mg/L.
The available options for `BAS_CRPUnits` are:

- mg/dL in which case `BAS_CRPResult` = 10 $\times$ `BAS_CRPEntered`
- mg/L or $\mu$g/mL in which case `BAS_CRPResult` = `BAS_CRPEntered`

Below is some example data.

```{r}
#| label: fig-example-data
#| fig-cap: Example data
all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  filter(!is.na(BAS_CRPResult)) |>
  select(BAS_CRPEntered, BAS_CRPUnits, BAS_CRPResult) |>
  head(5)
```

## Issue with Reported Units

It looks like there may be an issue with mis-specification of the reported units.
In many sites, it appears that results for `BAS_CRPResult` are inflated by a factor of 10 when `BAS_CRPEntered` is reported in mg/dL, suggesting that the units may have been mis-reported as mg/dL rather than mg/L.
However, this is not always completely clear and may only have occurred at specific sites or for a subset of individuals.

For example (@tbl-summaries), at Australian sites, for participants where the reported unit of entry was *mg/dL* the entered resuts had median 56 whereas for participants where the reported unit of entry was *mg/L* the median was similar at 56. Therefore, after transforming the *mg/dL* units to *mg/L* the median for `BAS_CRPResult` is 560 vs 56.
A similar issue is observed for data from New Zealand and Nepal.
The issue is less clear for sites in India, however, given the difference between the two groups, it looks as though some sites may have mis-reported units or that units may have been reported for some subset of participants.

See also @fig-crp-hist, @fig-ecdf-country, and @fig-ecdf-india-sites.

```{r}
#| label: tbl-summaries
#| tbl-cap: Sample summaries for CRP by country and reported units. Type "entered" corresponds to `BAS_CRPEntered` and "result" to `BAS_CRPResult`.
all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  filter(!is.na(BAS_CRPResult)) |>
  group_by(Country, BAS_CRPUnits) |>
  summarise(
    n = n(),
    median_result = median(BAS_CRPResult),
    min_result = min(BAS_CRPResult),
    max_result = max(BAS_CRPResult),
    median_entered = median(BAS_CRPEntered),
    min_entered = min(BAS_CRPEntered),
    max_entered = max(BAS_CRPEntered),
  ) |>
  ungroup() |>
  pivot_longer(median_result:max_entered, names_sep = "_", names_to = c("summary", "Type")) |>
  pivot_wider(names_from = summary, values_from = value) |>
  arrange(Country, Type, BAS_CRPUnits) |>
  kable(
    "latex",
    booktabs = TRUE,
    linesep = c("", "", "", "\\\\")
  ) |>
  kable_styling(latex_options = "HOLD_position")
```

```{r}
#| label: fig-crp-hist
#| code-summary: Histogram of CRP by reported units.
#| fig-cap: |
#|   Distribution of CRP (mg/L) by reported units (mg/L vs mg/dL).
#| fig-height: 2
p <- all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  filter(!is.na(BAS_CRPResult)) |>
  ggplot(aes(BAS_CRPResult)) +
  facet_wrap( ~ BAS_CRPUnits , scales = "free_y") +
  geom_histogram(bins = 30) +
  labs(x = "CRP result (mg/L)", y = "Frequency")
p
```

```{r}
#| label: fig-ecdf-country
#| fig-cap: Empirical Cumulative Distribution Function by country and reported units of CRP.
all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  filter(!is.na(BAS_CRPResult)) |>
  ggplot(aes(BAS_CRPResult)) +
  stat_ecdf(aes(colour = BAS_CRPUnits)) + 
  facet_wrap( ~ Country) +
  labs(x = "BAS_CRPResult (mg/L)", y = "eCDF") + 
  scale_x_log10()
```

```{r}
#| label: fig-ecdf-india-sites
#| fig-cap: Empirical Cumulative Distribution Function by sites in India and reported units of CRP.
all_data |>
  filter(ENR_rec == 1, WTH_FU == 0) |>
  filter(!is.na(BAS_CRPResult), Country == "IN") |>
  ggplot(aes(BAS_CRPResult)) +
  stat_ecdf(aes(colour = BAS_CRPUnits)) + 
  facet_wrap( ~ Location) +
  labs(x = "BAS_CRPResult (mg/L)", y = "eCDF") + 
  scale_x_log10()
```
